### 2022-02-17 Proposal.tex
created proposal

\documentclass{article}

%%% Packeges %%%
\usepackage[margin=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{scrextend}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[noend]{algpseudocode}
\usepackage{bm}
% \usepackage{pythonhighlight}

%%% Links %%%
\hypersetup{
    colorlinks=true,     
    urlcolor=blue,
}

%%% Formatting %%%
\setlength{\headheight}{25pt}
\pagestyle{fancy}
\lhead{Sacha Goldman, Shirley Wang, Yuchong Zhang} 
\rhead{CSC413 Project Proposal}
\setlength{\parskip}{1em}
% \setlength\parindent{0pt}

%%% Commands %%%
\newcommand{\powerset}{\mathcal P}
\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\Q}{\mathbb Q}
\newcommand{\Z}{\mathbb Z}
\newcommand{\N}{\mathbb N}
\newcommand{\E}{\mathbb E}
\renewcommand{\P}{\mathbb P}
\renewcommand{\Re}{\text{Re }}
\renewcommand{\Im}{\text{Im }}
\newcommand{\der}[2]{\frac{d #1}{d #2}}
\newcommand{\pder}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\iso}{\cong}
\newcommand{\divs}{\big\vert}
\newcommand{\boundry}{\partial}
\newcommand{\cross}{\times}
\newcommand\lit[1]{{\texttt{"#1"}}}
\newcommand{\norm}[1]{\left| \left| #1 \right| \right|}
\newcommand{\ip}[2]{\langle #1, #2 \rangle}
\newcommand{\lemma}[2]{\textbf{Lemma} \begin{indented} #1 \end{indented} \textbf{Proof of Lemma} \begin{indented} #2 \end{indented}}
\newcommand{\induction}[2]{\textbf{Base Case} \begin{indented} #1 \end{indented} \textbf{Inductive Case} \begin{indented} #2 \end{indented}}
\newcommand{\note}[1]{\textbf{Note:} #1}
\renewcommand{\phi}{\varphi}
\newcommand{\err}[1]{\overline{#1}}
\newcommand{\tr}{\text{trace}}

%%% Enviroments %%%
\newenvironment{pseudo}{\begin{algorithmic}[1]}{\end{algorithmic}}
\newenvironment{indented}[1][1.5]{\begin{addmargin}{#1em}}{\end{addmargin}}

%%% Document %%%
\begin{document}
\end{document}

### 2022-03-04 Proposal.tex
so much tex setup

@@
 
-%%% Packeges %%%
-\usepackage[margin=0.8in]{geometry}
+\PassOptionsToPackage{numbers, compress}{natbib}
+
+\usepackage[final]{proposal_neurips_2021}
+
+\bibliographystyle{abbrvnat}
+
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{enumitem}
-\usepackage{mathrsfs}
-\usepackage{graphicx}
-\usepackage{fancyhdr}
-\usepackage{scrextend}
+\usepackage[T1]{fontenc}
 \usepackage{hyperref}
-\usepackage{tikz}
-\usepackage[noend]{algpseudocode}
-\usepackage{bm}
-% \usepackage{pythonhighlight}
+\usepackage{url}
+\usepackage{booktabs}
+\usepackage{amsfonts}
+\usepackage{nicefrac}
+\usepackage{microtype}
+\usepackage{xcolor}
 
-%%% Links %%%
-\hypersetup{
-    colorlinks=true,     
-    urlcolor=blue,
+\title{Proposal: DINO Methods for Style Transfer}
+
+\author{
+  Sacha Goldman \\
+  Department of Computer Science\\ 
+  Department of Mathematics\\
+  University of Toronto\\
+  Toronto, ON M5S 1A1 \\
+  \texttt{sacha.goldman@mail.utoronto.ca} \\
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
 }
 
-%%% Formatting %%%
-\setlength{\headheight}{25pt}
-\pagestyle{fancy}
-\lhead{Sacha Goldman, Shirley Wang, Yuchong Zhang} 
-\rhead{CSC413 Project Proposal}
-\setlength{\parskip}{1em}
-% \setlength\parindent{0pt}
+\begin{document}
 
-%%% Commands %%%
-\newcommand{\powerset}{\mathcal P}
-\newcommand{\C}{\mathbb C}
-\newcommand{\R}{\mathbb R}
-\newcommand{\Q}{\mathbb Q}
-\newcommand{\Z}{\mathbb Z}
-\newcommand{\N}{\mathbb N}
-\newcommand{\E}{\mathbb E}
-\renewcommand{\P}{\mathbb P}
-\renewcommand{\Re}{\text{Re }}
-\renewcommand{\Im}{\text{Im }}
-\newcommand{\der}[2]{\frac{d #1}{d #2}}
-\newcommand{\pder}[2]{\frac{\partial #1}{\partial #2}}
-\newcommand{\iso}{\cong}
-\newcommand{\divs}{\big\vert}
-\newcommand{\boundry}{\partial}
-\newcommand{\cross}{\times}
-\newcommand\lit[1]{{\texttt{"#1"}}}
-\newcommand{\norm}[1]{\left| \left| #1 \right| \right|}
-\newcommand{\ip}[2]{\langle #1, #2 \rangle}
-\newcommand{\lemma}[2]{\textbf{Lemma} \begin{indented} #1 \end{indented} \textbf{Proof of Lemma} \begin{indented} #2 \end{indented}}
-\newcommand{\induction}[2]{\textbf{Base Case} \begin{indented} #1 \end{indented} \textbf{Inductive Case} \begin{indented} #2 \end{indented}}
-\newcommand{\note}[1]{\textbf{Note:} #1}
-\renewcommand{\phi}{\varphi}
-\newcommand{\err}[1]{\overline{#1}}
-\newcommand{\tr}{\text{trace}}
+\maketitle
 
-%%% Enviroments %%%
-\newenvironment{pseudo}{\begin{algorithmic}[1]}{\end{algorithmic}}
-\newenvironment{indented}[1][1.5]{\begin{addmargin}{#1em}}{\end{addmargin}}
+\begin{abstract}
 
-%%% Document %%%
-\begin{document}
+\end{abstract}
+
+\section{Introduction}
+
+\section{Related Works}
+
+\section{Method}
+
+\medskip
+
+% Our current sources
+\nocite{*}
+
+\bibliography{bib}
+
 \end{document}

### 2022-03-04 Proposal.tex
began introduction

@@
 \section{Introduction}
+Style transfer is the problem of changing an image's artistic style while maintaining its ``content'', namely the object it depicts.
+Conventional models use CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image.
+However, it has been shown that due to the locality resulting from shared weights, CNN struggles to capture global information of input images and suffers from feature losses \cite{ImageStyleTransformer}.
+To resolve these issues, models that use Transformers instead of CNN for feature and style extraction have been proposed and shown improved results \cite{ImageStyleTransformer}.
+The authors of \cite{ImageStyleTransformer} use
 

### 2022-03-04 Proposal.tex
Method Subsections
method 1 proposal

@@
 
+We have four different idea for brining the success of the DINO method to the domain of style transfer.
+
+\subsection{DINO Content Encoder}
+
+We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer paradigm.
+The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
+
+\subsection{Pre-trained DINO Content Encoder}
+
+\subsection{DINO Training for Encoders}
+
+\subsection{Modified DINO Training for Encoders}
+
 \medskip

### 2022-03-04 Proposal.tex
some related works

--- 2022-03-04 Proposal.tex
@@
 
+\cite{dino} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student approach.
+The student gets a difficult version (lots of augmentation) of the image while the teacher gets an easy version (minimal augmentation), and then the models are trained to aim for the same feature representation through cross entropy loss.
+Their experiment results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing very well as classifiers.
+Our motivation for this project stems from how this DINO method has shown to have been able to achieve a better feature representation than supervised vision transformers, and we would like to apply this in a new domain: image style transfer.
+
+Self-supervised learning has been a common technique used in style transfer, due to the obvious lack of target images available for a task like this.
+It becomes necessary to find ways for the model to supervise its own outputs.
+Usual methods (add sources) involve checking the outputs of VGG for consistency in style and context.
+
+(write something about the Style Transfer Transformer)
+
+(write something about different style transfer methods)
+
 \section{Method}

### 2022-03-04 Proposal.tex
method 2 proposal

--- 2022-03-04 Proposal.tex
@@
 
-We have four different idea for brining the success of the DINO method to the domain of style transfer.
+We have four different idea for bringing the success of the DINO method to the domain of style transfer.
 
-\subsection{DINO Content Encoder}
+\subsection{Frozen DINO Content Encoder}
 
-We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer paradigm.
+We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer training paradigm.
 The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
 
-\subsection{Pre-trained DINO Content Encoder}
+\subsection{DINO Weight Initialized Content Encoder}
+
+We use a transformer trained by DINO as the initial weights for the content encoder but we run the style transfer training paradigm on both encoders and the decoder, effectively using the weights from DINO as initial weights.
+We expect this to converge to a different optima because transformers have many local optima.
+We hope that the robust abstractions from the DINO training process lead to better style transfer.
 

### 2022-03-04 Proposal.tex
finished intro

@@
   \texttt{sacha.goldman@mail.utoronto.ca} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
+  \And
+  Yuchong Zhang \\
+  Department of Computer Science \\
+  Department of Mathematics \\
+  University of Toronoto \\
+  Toronto, ON, M5S 1A1 \\
+  \texttt{yuchongz.zhang@mail.utoronto.ca} \\
   % \And
@@
 To resolve these issues, models that use Transformers instead of CNN for feature and style extraction have been proposed and shown improved results \cite{ImageStyleTransformer}.
-The authors of \cite{ImageStyleTransformer} use
+The model StyTr proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder.
+In our project, we will substitute the DINO model proposed in \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
+DINO method is good at extracting content even if the input images are distorted or partial.
+So in particular, we will implement the models and conduct experiments to explore the following questions:
+\begin{enumerate}
+  \item By using DINO to extract content, can we obtain a style transfer that is robust to distortions of content images?
+  \item Does DINO's ability to capture an image's global property from local pieces give it more robustness as a style encoder?
+\end{enumerate}
 
@@
 \section{Method}
-
-We have four different idea for bringing the success of the DINO method to the domain of style transfer.
-
-\subsection{Frozen DINO Content Encoder}
-
-We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer training paradigm.
-The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
-
-\subsection{DINO Weight Initialized Content Encoder}
-
-We use a transformer trained by DINO as the initial weights for the content encoder but we run the style transfer training paradigm on both encoders and the decoder, effectively using the weights from DINO as initial weights.
-We expect this to converge to a different optima because transformers have many local optima.
-We hope that the robust abstractions from the DINO training process lead to better style transfer.
-
-\subsection{DINO Training for Encoders}
-
-\subsection{Modified DINO Training for Encoders}
 

### 2022-03-04 Proposal.tex

@@
 
+We have four different idea for bringing the success of the DINO method to the domain of style transfer.
+
+\subsection{Frozen DINO Content Encoder}
+
+We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer training paradigm.
+The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
+
+\subsection{DINO Weight Initialized Content Encoder}
+
+We use a transformer trained by DINO as the initial weights for the content encoder but we run the style transfer training paradigm on both encoders and the decoder, effectively using the weights from DINO as initial weights.
+We expect this to converge to a different optima because transformers have many local optima.
+We hope that the robust abstractions from the DINO training process lead to better style transfer.
+
+\subsection{DINO Training for Encoders}
+
+\subsection{Modified DINO Training for Encoders}
+
 \medskip

### 2022-03-04 Proposal.tex
related works

--- 2022-03-04 Proposal.tex
@@
 
+\cite{DINO} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student approach.
+The student gets a difficult version (lots of augmentation) of the image while the teacher gets an easy version (minimal augmentation), and then the models are trained to aim for the same feature representation through cross entropy loss.
+Their experiment results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing very well as classifiers.
+Our motivation for this project stems from how this DINO method has shown to have been able to achieve a better feature representation than supervised vision transformers, and we would like to apply this in a new domain: image style transfer.
+
+Self-supervised learning has been a common technique used in style transfer, due to the obvious lack of target images available for a task like this.
+It becomes necessary to find ways for the model to supervise its own outputs.
+Usual methods (add sources) involve checking the outputs of VGG for consistency in style and context.
+\cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
+Transformers have been a hot rising topic in computer vision, and they claim that using transformers for style transfer result in a decrease in content leak, as well as achieving unbiased stylization.
+
+It becomes integral for there to be good feature representations of the content and style to construct a good style-transferred image.
+We believe that making use of pretrained DINO ViT models, as well as using the DINO method itself during training, can help achieve this.
+
 \section{Method}
 
-We have four different idea for bringing the success of the DINO method to the domain of style transfer.
+We have four different idea for brining the success of the DINO method to the domain of style transfer.
 
-\subsection{Frozen DINO Content Encoder}
+\subsection{DINO Content Encoder}
 
-We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer training paradigm.
+We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer paradigm.
 The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
 
-\subsection{DINO Weight Initialized Content Encoder}
-
-We use a transformer trained by DINO as the initial weights for the content encoder but we run the style transfer training paradigm on both encoders and the decoder, effectively using the weights from DINO as initial weights.
-We expect this to converge to a different optima because transformers have many local optima.
-We hope that the robust abstractions from the DINO training process lead to better style transfer.
+\subsection{Pre-trained DINO Content Encoder}
 

### 2022-03-04 Proposal.tex
method 3 proposal

--- 2022-03-04 Proposal.tex
@@
 
-\cite{DINO} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student approach.
-The student gets a difficult version (lots of augmentation) of the image while the teacher gets an easy version (minimal augmentation), and then the models are trained to aim for the same feature representation through cross entropy loss.
-Their experiment results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing very well as classifiers.
-Our motivation for this project stems from how this DINO method has shown to have been able to achieve a better feature representation than supervised vision transformers, and we would like to apply this in a new domain: image style transfer.
-
-Self-supervised learning has been a common technique used in style transfer, due to the obvious lack of target images available for a task like this.
-It becomes necessary to find ways for the model to supervise its own outputs.
-Usual methods (add sources) involve checking the outputs of VGG for consistency in style and context.
-\cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
-Transformers have been a hot rising topic in computer vision, and they claim that using transformers for style transfer result in a decrease in content leak, as well as achieving unbiased stylization.
-
-It becomes integral for there to be good feature representations of the content and style to construct a good style-transferred image.
-We believe that making use of pretrained DINO ViT models, as well as using the DINO method itself during training, can help achieve this.
-
 \section{Method}
@@
 
+For the purpose of training we add a teacher content encoder and a teacher style encoder.
+Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images.
+We then add to the loss from the standard style transfer to the cross entropy loss between the teacher encodings and and the student encodings.
+This forces the students to learn distillations of the original images.
+We expect this to work better for the style encoder, because style is a global property of an image, so we may only apply this method for the style encoder.
+
 \subsection{Modified DINO Training for Encoders}

### 2022-03-04 Proposal.tex
some typos

@@
   \texttt{yuchongz.zhang@mail.utoronto.ca} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
+  \And
+  Shirley Wang \\
+  Department of Computer Science \\
+  University of Toronto \\
+  Toronto, ON M5S 1A1 \\
+  \texttt{shirlsyuemeng.wang@mail.utoronto.ca} \\
 }
@@
 
-We have four different idea for bringing the success of the DINO method to the domain of style transfer.
+We have four different ideas for bringing the success of the DINO method to the style transfer task.
 
@@
 
-We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer training paradigm.
+We initialize the content encoder with the DINO pretrained vision transformer and freeze its weights, while training the style encoder and decoder using the regular style transfer training paradigm.
 The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
@@
 
-We use a transformer trained by DINO as the initial weights for the content encoder but we run the style transfer training paradigm on both encoders and the decoder, effectively using the weights from DINO as initial weights.
+We initialize the content encoder with the DINO pretrained vision transformer, but we run the style transfer training paradigm on both encoders and the decoder.
 We expect this to converge to a different optima because transformers have many local optima.
@@
 
-For the purpose of training we add a teacher content encoder and a teacher style encoder.
+For the purpose of DINO training we add a teacher content encoder and a teacher style encoder.
 Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images.

### 2022-03-04 Proposal.tex
finished abstract
method 4 proposal

--- 2022-03-04 Proposal.tex
@@
 
+This method is similar to the previous expect instead of taking the cross entropy between the encodings we take apply the decoder transformer to the encodings from the teacher encoders, to yield a new image.
+We then add to our loss the distance between the teacher image and the student image.
+The precise distance metric used here is to be determined through experimentation.
+This will allow the encoders to distill the important pieces of the stylized image.
+This method may suffer from being very expensive to train, which may cause issues.
+We also may only apply this to the style encoder.
+
 \medskip

### 2022-03-04 Proposal.tex

--- 2022-03-04 Proposal.tex
@@
 \begin{abstract}
-
+We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr \cite{ImageStyleTransformer}, a style transferer that renders images with artistic style, and explore the robustness of the resulting model.
 \end{abstract}

### 2022-03-04 Proposal.tex
added a source
proposal edits

--- 2022-03-04 Proposal.tex
@@
 \begin{abstract}
-
+We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr \cite{ImageStyleTransformer}, a style transferer that renders images with artistic style, and explore the nature and robustness of the resulting model.
 \end{abstract}
@@
 Style transfer is the problem of changing an image's artistic style while maintaining its ``content'', namely the object it depicts.
-Conventional models use CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image.
-However, it has been shown that due to the locality resulting from shared weights, CNN struggles to capture global information of input images and suffers from feature losses \cite{ImageStyleTransformer}.
-To resolve these issues, models that use Transformers instead of CNN for feature and style extraction have been proposed and shown improved results \cite{ImageStyleTransformer}.
+Conventional models use a CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image.
+However, it has been shown that due to the locality resulting from shared weights, CNN based models struggle to capture global information of input images and suffer from feature losses \cite{ImageStyleTransformer}.
+To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results \cite{ImageStyleTransformer}.
 The model StyTr proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder.
-In our project, we will substitute the DINO model proposed in \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
-DINO method is good at extracting content even if the input images are distorted or partial.
-So in particular, we will implement the models and conduct experiments to explore the following questions:
+In our project, we will substitute the methods DINO from \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
+The DINO method is good at extracting content even if the input images are distorted or partial, so in particular, we will implement the models and conduct experiments to explore the following questions:
 \begin{enumerate}
-  \item By using DINO to extract content, can we obtain a style transfer that is robust to distortions of content images?
+  \item By using DINO to extract content, can we obtain a style transfer that is more robust to distortion of the content image?
   \item Does DINO's ability to capture an image's global property from local pieces give it more robustness as a style encoder?
+  \item Are the results of this new style transfer method better than previous methods?
 \end{enumerate}
@@
 
-\cite{DINO} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student approach.
+\cite{DINO} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student paradigm.
 The student gets a difficult version (lots of augmentation) of the image while the teacher gets an easy version (minimal augmentation), and then the models are trained to aim for the same feature representation through cross entropy loss.
-Their experiment results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing very well as classifiers.
-Our motivation for this project stems from how this DINO method has shown to have been able to achieve a better feature representation than supervised vision transformers, and we would like to apply this in a new domain: image style transfer.
+Their experimental results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing as very accurate classifiers.
+In this project, we aim to apply the better feature representation that the DINO method yields (over supervised vision transformers), to the domain of image style transfer.
 
-Self-supervised learning has been a common technique used in style transfer, due to the obvious lack of target images available for a task like this.
+Self-supervised learning is a common technique used in style transfer, due to the obvious lack of target images available for a task of this nature.
 It becomes necessary to find ways for the model to supervise its own outputs.
-Usual methods (add sources) involve checking the outputs of VGG for consistency in style and context.
+Usual methods \cite{CNNStyleTransfer} involve checking the outputs of VGG for consistency in style and context.
 \cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
-Transformers have been a hot rising topic in computer vision, and they claim that using transformers for style transfer result in a decrease in content leak, as well as achieving unbiased stylization.
+Transformers have been a hot rising topic in computer vision, and they claim that their method of using transformers for style transfer results in a decrease in content leak, as well as acheives unbiased stylization.
 
@@
 
-We initialize the content encoder with the DINO pretrained vision transformer and freeze its weights, while training the style encoder and decoder using the regular style transfer training paradigm.
-The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.
+We initialize the content encoder with the DINO pretrained vision transformer and freeze its weights.
+Then we train the style encoder and decoder using the regular style transfer training paradigm from \cite{ImageStyleTransformer}.
+The idea being that the DINO model's robust feature vectors may act as powerful abstractions of the content of the images, that can be used for creating a new stylized image.
 
@@
 We expect this to converge to a different optima because transformers have many local optima.
-We hope that the robust abstractions from the DINO training process lead to better style transfer.
+We hope that the robust abstractions from the DINO training process lead to better style transfer after training.
 
@@
 Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images.
-We then add to the loss from the standard style transfer to the cross entropy loss between the teacher encodings and and the student encodings.
+We then add the loss from the standard style transfer and the cross entropy loss between the teacher encodings and and the student encodings.
 This forces the students to learn distillations of the original images.
@@
 \subsection{Modified DINO Training for Encoders}
+
+This method is similar to the previous expect instead of taking the cross entropy between the encodings we take apply the decoder transformer to the encodings from the teacher encoders, to yield a new image.
+We then use the distance between the teacher image and the student image in our loss.
+The precise distance metric used here is to be determined through experimentation.
+This will allow the encoders to distill the important pieces of the stylized image.
+This method may suffer from being very expensive to train.
+We also may only apply this to the style encoder.
 

### 2022-03-04 Proposal.tex
finished abstract

--- 2022-03-04 Proposal.tex
@@
 \begin{abstract}
-We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr \cite{ImageStyleTransformer}, a style transferer that renders images with artistic style, and explore the robustness of the resulting model.
+We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr \cite{ImageStyleTransformer}, a style transferer that renders images with artistic styles, and explore the robustness of the resulting model.
 \end{abstract}
@@
 It becomes necessary to find ways for the model to supervise its own outputs.
-Usual methods (add sources) involve checking the outputs of VGG for consistency in style and context.
+Usual methods \cite{CNNStyleTransfer} involve checking the outputs of VGG for consistency in style and context.
 \cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.

### 2022-03-04 Proposal.tex
some typos and refactorings

--- 2022-03-04 Proposal.tex
@@
 Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images.
-We then add the loss from the standard style transfer and the cross entropy loss between the teacher encodings and and the student encodings.
+We then add together the loss from the standard style transfer and the cross entropy loss between the teacher encodings and the student encodings.
 This forces the students to learn distillations of the original images.
@@
 
-This method is similar to the previous expect instead of taking the cross entropy between the encodings we take apply the decoder transformer to the encodings from the teacher encoders, to yield a new image.
+This method is similar to the previous, except that instead of taking the cross entropy between the encodings, we take apply the decoder transformer to the encodings from both the teacher and student encoders, which would yield a teacher image and a student image.
 We then use the distance between the teacher image and the student image in our loss.

### 2022-03-04 Proposal.tex
small wording changes

--- 2022-03-04 Proposal.tex
@@
 \begin{abstract}
-We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr \cite{ImageStyleTransformer}, a style transferer that renders images with artistic style, and explore the nature and robustness of the resulting model.
+We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr2 \cite{ImageStyleTransformer}, a style transfer transformer that renders images with artistic style, and explore the nature and robustness of the resulting model.
 \end{abstract}
@@
 To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results \cite{ImageStyleTransformer}.
-The model StyTr proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder.
-In our project, we will substitute the methods DINO from \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
+The model StyTr2 proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder.
+In our project, we will substitute the DINO method and models from \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
 The DINO method is good at extracting content even if the input images are distorted or partial, so in particular, we will implement the models and conduct experiments to explore the following questions:
@@
 
-\subsection{DINO Weight Initialized Content Encoder}
+\subsection{Initial Pretrained DINO Content Encoder}
 

### 2022-03-27 main_dino.py
added relevant files from repos with some bug fixes

@@ -1,0 +1,471 @@
+# Copyright (c) Facebook, Inc. and its affiliates.
+# 
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+# 
+#     http://www.apache.org/licenses/LICENSE-2.0
+# 
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+import argparse
+import os
+import sys
+import datetime
+import time
+import math
+import json
+from pathlib import Path
+
+import numpy as np
+from PIL import Image
+import torch
+import torch.nn as nn
+import torch.distributed as dist
+import torch.backends.cudnn as cudnn
+import torch.nn.functional as F
+from torchvision import datasets, transforms
+from torchvision import models as torchvision_models
+
+import util.dino_utils as util
+import vision_transformer as vits
+from vision_transformer import DINOHead
+
+torchvision_archs = sorted(name for name in torchvision_models.__dict__
+    if name.islower() and not name.startswith("__")
+    and callable(torchvision_models.__dict__[name]))
+
+def get_args_parser():
+    parser = argparse.ArgumentParser('DINO', add_help=False)
+
+    # Model parameters
+    parser.add_argument('--arch', default='vit_small', type=str,
+        choices=['vit_tiny', 'vit_small', 'vit_base', 'xcit', 'deit_tiny', 'deit_small'] \
+                + torchvision_archs + torch.hub.list("facebookresearch/xcit:main"),
+        help="""Name of architecture to train. For quick experiments with ViTs,
+        we recommend using vit_tiny or vit_small.""")
+    parser.add_argument('--patch_size', default=16, type=int, help="""Size in pixels
+        of input square patches - default 16 (for 16x16 patches). Using smaller
+        values leads to better performance but requires more memory. Applies only
+        for ViTs (vit_tiny, vit_small and vit_base). If <16, we recommend disabling
+        mixed precision training (--use_fp16 false) to avoid unstabilities.""")
+    parser.add_argument('--out_dim', default=65536, type=int, help="""Dimensionality of
+        the DINO head output. For complex and large datasets large values (like 65k) work well.""")
[…]

### 2022-03-27 models/StyTR.py

@@ -1,0 +1,233 @@
+import torch
+import torch.nn.functional as F
+from torch import nn
+import numpy as np
+from util import box_ops
+from util.misc import (NestedTensor, nested_tensor_from_tensor_list,
+                       accuracy, get_world_size, interpolate,
+                       is_dist_avail_and_initialized)
+from function import normal,normal_style
+from function import calc_mean_std
+import scipy.stats as stats
+from models.ViT_helper import DropPath, to_2tuple, trunc_normal_
+
+class PatchEmbed(nn.Module):
+    """ Image to Patch Embedding
+    """
+    def __init__(self, img_size=256, patch_size=8, in_chans=3, embed_dim=512):
+        super().__init__()
+        img_size = to_2tuple(img_size)
+        patch_size = to_2tuple(patch_size)
+        num_patches = (img_size[1] // patch_size[1]) * (img_size[0] // patch_size[0])
+        self.img_size = img_size
+        self.patch_size = patch_size
+        self.num_patches = num_patches
+        
+        self.proj = nn.Conv2d(in_chans, embed_dim, kernel_size=patch_size, stride=patch_size)
+        self.up1 = nn.Upsample(scale_factor=2, mode='nearest')
+
+    def forward(self, x):
+        B, C, H, W = x.shape
+        x = self.proj(x)
+
+        return x
+
+
+decoder = nn.Sequential(
+    nn.ReflectionPad2d((1, 1, 1, 1)),
+    nn.Conv2d(512, 256, (3, 3)),
+    nn.ReLU(),
+    nn.Upsample(scale_factor=2, mode='nearest'),
+    nn.ReflectionPad2d((1, 1, 1, 1)),
+    nn.Conv2d(256, 256, (3, 3)),
+    nn.ReLU(),
+    nn.ReflectionPad2d((1, 1, 1, 1)),
+    nn.Conv2d(256, 256, (3, 3)),
+    nn.ReLU(),
+    nn.ReflectionPad2d((1, 1, 1, 1)),
+    nn.Conv2d(256, 256, (3, 3)),
+    nn.ReLU(),
+    nn.ReflectionPad2d((1, 1, 1, 1)),
+    nn.Conv2d(256, 128, (3, 3)),
+    nn.ReLU(),
+    nn.Upsample(scale_factor=2, mode='nearest'),
+    nn.ReflectionPad2d((1, 1, 1, 1)),
+    nn.Conv2d(128, 128, (3, 3)),
+    nn.ReLU(),
[…]

### 2022-03-27 models/transformer.py

@@ -1,0 +1,324 @@
+import copy
+from typing import Optional, List
+
+import torch
+import torch.nn.functional as F
+from torch import nn, Tensor
+from function import normal,normal_style
+import numpy as np
+import os
+device = torch.device("cuda:2" if torch.cuda.is_available() else "cpu")
+os.environ["CUDA_VISIBLE_DEVICES"] = "2, 3"
+class Transformer(nn.Module):
+
+    def __init__(self, d_model=512, nhead=8, num_encoder_layers=3,
+                 num_decoder_layers=3, dim_feedforward=2048, dropout=0.1,
+                 activation="relu", normalize_before=False,
+                 return_intermediate_dec=False):
+        super().__init__()
+
+        encoder_layer = TransformerEncoderLayer(d_model, nhead, dim_feedforward,
+                                                dropout, activation, normalize_before)
+        encoder_norm = nn.LayerNorm(d_model) if normalize_before else None
+        
+        # TODO: these encoders are the things we talked about in our proposal
+        self.encoder_c = TransformerEncoder(encoder_layer, num_encoder_layers, encoder_norm)
+        self.encoder_s = TransformerEncoder(encoder_layer, num_encoder_layers, encoder_norm)
+
+        decoder_layer = TransformerDecoderLayer(d_model, nhead, dim_feedforward,
+                                                dropout, activation, normalize_before)
+        decoder_norm = nn.LayerNorm(d_model)
+        self.decoder = TransformerDecoder(decoder_layer, num_decoder_layers, decoder_norm,
+                                          return_intermediate=return_intermediate_dec)
+
+        self._reset_parameters()
+
+        self.d_model = d_model
+        self.nhead = nhead
+
+        self.new_ps = nn.Conv2d(512 , 512 , (1,1))
+        self.averagepooling = nn.AdaptiveAvgPool2d(18)
+
+    def _reset_parameters(self):
+        for p in self.parameters():
+            if p.dim() > 1:
+                nn.init.xavier_uniform_(p)
+
+    def forward(self, style, mask , content, pos_embed_c, pos_embed_s):
+
+        # content-aware positional embedding
+        content_pool = self.averagepooling(content)       
+        pos_c = self.new_ps(content_pool)
+        pos_embed_c = F.interpolate(pos_c, mode='bilinear',size= style.shape[-2:])
+
+        ###flatten NxCxHxW to HWxNxC     
[…]

### 2022-03-27 train.py

@@ -1,0 +1,210 @@
+import argparse
+import os
+import torch
+import torch.nn as nn
+import torch.utils.data as data
+from PIL import Image
+from PIL import ImageFile
+from tensorboardX import SummaryWriter
+from torchvision import transforms
+from tqdm import tqdm
+from pathlib import Path
+import models.transformer as transformer
+import models.StyTR  as StyTR 
+from sampler import InfiniteSamplerWrapper
+from torchvision.utils import save_image
+
+
+def train_transform():
+    transform_list = [
+        transforms.Resize(size=(512, 512)),
+        transforms.RandomCrop(256),
+        transforms.ToTensor()
+    ]
+    return transforms.Compose(transform_list)
+
+
+class FlatFolderDataset(data.Dataset):
+    def __init__(self, root, transform):
+        super(FlatFolderDataset, self).__init__()
+        self.root = root
+        print(self.root)
+        self.path = os.listdir(self.root)
+        if os.path.isdir(os.path.join(self.root,self.path[0])):
+            self.paths = []
+            for file_name in os.listdir(self.root):
+                for file_name1 in os.listdir(os.path.join(self.root,file_name)):
+                    self.paths.append(self.root+"/"+file_name+"/"+file_name1)             
+        else:
+            self.paths = list(Path(self.root).glob('*'))
+        self.transform = transform
+    def __getitem__(self, index):
+        path = self.paths[index]
+        img = Image.open(str(path)).convert('RGB')
+        img = self.transform(img)
+        return img
+    def __len__(self):
+        return len(self.paths)
+    def name(self):
+        return 'FlatFolderDataset'
+
+def adjust_learning_rate(optimizer, iteration_count):
+    """Imitating the original implementation"""
+    lr = 2e-4 / (1.0 + args.lr_decay * (iteration_count - 1e4))
+    for param_group in optimizer.param_groups:
+        param_group['lr'] = lr
+
+def warmup_learning_rate(optimizer, iteration_count):
+    """Imitating the original implementation"""
+    lr = args.lr * 0.1 * (1.0 + 3e-4 * iteration_count)
+    # print(lr)
+    for param_group in optimizer.param_groups:
+        param_group['lr'] = lr
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser()
+    # Basic options
+    parser.add_argument('--content_dir', default='./datasets/train2014', type=str,   
+                        help='Directory path to a batch of content images')
[…]

### 2022-03-27 util/misc.py

@@ -1,0 +1,470 @@
+# Copyright (c) Facebook, Inc. and its affiliates. All Rights Reserved
+"""
+Misc functions, including distributed helpers.
+
+Mostly copy-paste from torchvision references.
+"""
+import os
+import subprocess
+import time
+from collections import defaultdict, deque
+import datetime
+import pickle
+from typing import Optional, List
+
+import torch
+import torch.distributed as dist
+from torch import Tensor
+
+# needed due to empty tensor bug in pytorch and torchvision 0.5
+import torchvision
+"""
+if float(torchvision.__version__[:3]) < 0.7:
+    from torchvision.ops import _new_empty_tensor
+    from torchvision.ops.misc import _output_size
+"""
+
+class SmoothedValue(object):
+    """Track a series of values and provide access to smoothed values over a
+    window or the global series average.
+    """
+
+    def __init__(self, window_size=20, fmt=None):
+        if fmt is None:
+            fmt = "{median:.4f} ({global_avg:.4f})"
+        self.deque = deque(maxlen=window_size)
+        self.total = 0.0
+        self.count = 0
+        self.fmt = fmt
+
+    def update(self, value, n=1):
+        self.deque.append(value)
+        self.count += n
+        self.total += value * n
+
+    def synchronize_between_processes(self):
+        """
+        Warning: does not synchronize the deque!
+        """
+        if not is_dist_avail_and_initialized():
+            return
+        t = torch.tensor([self.count, self.total], dtype=torch.float64, device='cuda')
+        dist.barrier()
+        dist.all_reduce(t)
+        t = t.tolist()
+        self.count = int(t[0])
+        self.total = t[1]
+
+    @property
+    def median(self):
+        d = torch.tensor(list(self.deque))
+        return d.median().item()
+
+    @property
+    def avg(self):
+        d = torch.tensor(list(self.deque), dtype=torch.float32)
+        return d.mean().item()
+
+    @property
+    def global_avg(self):
+        return self.total / self.count
+
+    @property
+    def max(self):
+        return max(self.deque)
+
+    @property
+    def value(self):
+        return self.deque[-1]
+
+    def __str__(self):
+        return self.fmt.format(
+            median=self.median,
+            avg=self.avg,
+            global_avg=self.global_avg,
+            max=self.max,
+            value=self.value)
+
+
+def all_gather(data):
+    """
[…]

### 2022-03-27 paper/Paper.tex
moved paper and proposal files to their own folders

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2021

% ready for submission
\usepackage{neurips_2021}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2021}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2021}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2021}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

\title{Formatting Instructions For NeurIPS 2021}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Submission of papers to NeurIPS 2021}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NeurIPS 2021 must be prepared according to the
instructions presented here. Papers may only be up to {\bf nine} pages long,
including figures. Additional pages \emph{containing only acknowledgments and
references} are allowed. Papers that exceed the page limit will not be
reviewed, or in any other way considered for presentation at the conference.

The margins in 2021 are the same as those in 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
  \url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2021.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2021 is \verb+neurips_2021.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{Preprint option}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2021.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2021+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2021}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
  acceptable for NeurIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\begin{ack}
Use unnumbered first level headings for the acknowledgments. All acknowledgments
go at the end of the paper before the list of references. Moreover, you are required to declare
funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2021/PaperInformation/FundingDisclosure}.

Do {\bf not} include this section in the anonymized submission, only in the final paper. You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
\end{ack}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
Note that the Reference section does not count towards the page limit.
\medskip

{
\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Checklist}

%%% BEGIN INSTRUCTIONS %%%
The checklist follows the references.  Please
read the checklist guidelines carefully for information on how to answer these
questions.  For each question, change the default \answerTODO{} to \answerYes{},
\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
justification to your answer}, either by referencing the appropriate section of
your paper or providing a brief inline description.  For example:
\begin{itemize}
  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
  \item Did you include the license to the code and datasets? \answerNA{}
\end{itemize}
Please do not modify the questions and only use the provided macros for your
answers.  Note that the Checklist section does not count towards the page
limit.  In your paper, please delete this instructions block and only keep the
Checklist section heading above along with the questions/answers below.
%%% END INSTRUCTIONS %%%

\begin{enumerate}

\item For all authors...
\begin{enumerate}
  \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
    \answerTODO{}
  \item Did you describe the limitations of your work?
    \answerTODO{}
  \item Did you discuss any potential negative societal impacts of your work?
    \answerTODO{}
  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
    \answerTODO{}
\end{enumerate}

\item If you are including theoretical results...
\begin{enumerate}
  \item Did you state the full set of assumptions of all theoretical results?
    \answerTODO{}
	\item Did you include complete proofs of all theoretical results?
    \answerTODO{}
\end{enumerate}

\item If you ran experiments...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerTODO{}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerTODO{}
	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerTODO{}
	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerTODO{}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerTODO{}
  \item Did you mention the license of the assets?
    \answerTODO{}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerTODO{}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerTODO{}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerTODO{}
\end{enumerate}

\item If you used crowdsourcing or conducted research with human subjects...
\begin{enumerate}
  \item Did you include the full text of instructions given to participants and screenshots, if applicable?
    \answerTODO{}
  \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
    \answerTODO{}
  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
    \answerTODO{}
\end{enumerate}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Appendix}

Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\end{document}

### 2022-03-27 main_dino.py
added some notes and TODOs

@@ -1,3 +1,8 @@
+"""
+TODO: use this as a basis in the train file to add DINO training to the style transfer stuff
+"""
+
+
 # Copyright (c) Facebook, Inc. and its affiliates.
 # 
 # Licensed under the Apache License, Version 2.0 (the "License");

### 2022-03-27 models/transformer.py

@@ -22,6 +22,7 @@ class Transformer(nn.Module):
         encoder_norm = nn.LayerNorm(d_model) if normalize_before else None
         
         # TODO: these encoders are the things we talked about in our proposal
+        # replaye with DINO through a flag
         self.encoder_c = TransformerEncoder(encoder_layer, num_encoder_layers, encoder_norm)
         self.encoder_s = TransformerEncoder(encoder_layer, num_encoder_layers, encoder_norm)
 

### 2022-03-27 train.py

@@ -1,3 +1,9 @@
+"""
+TODO: add DINO training as a possible thing through a flag
+
+TODO: add loss function here, take it out of the model
+"""
+
 import argparse
 import os
 import torch

### 2022-03-27 util/dino_utils.py

@@ -1,3 +1,7 @@
+"""
+NOTE: The original utils.py file from the dino repo, some util functions for training
+"""
+
 # Copyright (c) Facebook, Inc. and its affiliates.
 # 
 # Licensed under the Apache License, Version 2.0 (the "License");

### 2022-03-27 vision_transformer.py

@@ -1,0 +1,297 @@
+"""
+NOTE: This file is only here if you want to try running main_dino.py to see how it works.
+It's not something we'll be using.
+"""
+
+
+# Copyright (c) Facebook, Inc. and its affiliates.
+# 
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+# 
+#     http://www.apache.org/licenses/LICENSE-2.0
+# 
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+"""
+Mostly copy-paste from timm library.
+https://github.com/rwightman/pytorch-image-models/blob/master/timm/models/vision_transformer.py
+"""
+import math
+from functools import partial
+
+import torch
+import torch.nn as nn
+
+from util.dino_utils import trunc_normal_
+
+
+def drop_path(x, drop_prob: float = 0., training: bool = False):
+    if drop_prob == 0. or not training:
+        return x
+    keep_prob = 1 - drop_prob
+    shape = (x.shape[0],) + (1,) * (x.ndim - 1)  # work with diff dim tensors, not just 2D ConvNets
+    random_tensor = keep_prob + torch.rand(shape, dtype=x.dtype, device=x.device)
+    random_tensor.floor_()  # binarize
+    output = x.div(keep_prob) * random_tensor
+    return output
+
+
+class DropPath(nn.Module):
+    """Drop paths (Stochastic Depth) per sample  (when applied in main path of residual blocks).
+    """
+    def __init__(self, drop_prob=None):
+        super(DropPath, self).__init__()
+        self.drop_prob = drop_prob
+
+    def forward(self, x):
+        return drop_path(x, self.drop_prob, self.training)
+
+
+class Mlp(nn.Module):
+    def __init__(self, in_features, hidden_features=None, out_features=None, act_layer=nn.GELU, drop=0.):
+        super().__init__()
+        out_features = out_features or in_features
+        hidden_features = hidden_features or in_features
[…]

### 2022-03-27 train.py
more comments

@@ -6,20 +6,20 @@ TODO: add loss function here, take it out of the model
 
 import argparse
 import os
+from tqdm import tqdm
+from pathlib import Path
 import torch
 import torch.nn as nn
 import torch.utils.data as data
+from torchvision import transforms
+from torchvision.utils import save_image
 from PIL import Image
 from PIL import ImageFile
 from tensorboardX import SummaryWriter
-from torchvision import transforms
-from tqdm import tqdm
-from pathlib import Path
+
 import models.transformer as transformer
 import models.StyTR  as StyTR 
 from sampler import InfiniteSamplerWrapper
-from torchvision.utils import save_image
-
 
 def train_transform():
     transform_list = [
@@ -73,9 +73,9 @@ if __name__ == '__main__':
     # Basic options
     parser.add_argument('--content_dir', default='./datasets/train2014', type=str,   
                         help='Directory path to a batch of content images')
-    parser.add_argument('--style_dir', default='./datasets/Images', type=str,  #wikiart dataset crawled from https://www.wikiart.org/
+    parser.add_argument('--style_dir', default='./datasets/Images', type=str,
                         help='Directory path to a batch of style images')
-    parser.add_argument('--vgg', type=str, default='./experiments/vgg_normalised.pth')  #run the train.py, please download the pretrained vgg checkpoint
+    parser.add_argument('--vgg', type=str, default='./weights/vgg_normalised.pth')
 
     # training options
     parser.add_argument('--save_dir', default='./experiments',
@@ -94,18 +94,28 @@ if __name__ == '__main__':
                             help="Type of positional embedding to use on top of the image features")
     parser.add_argument('--hidden_dim', default=512, type=int,
                             help="Size of the embeddings (dimension of the transformer)")
+
+    # add additional flags for other experiments
+    parser.add_argument('--dino_encoder', default="none", type=str, help="Use a pretrained DINO encoder", choices=("none", "vits16", "vits8", "vitb16", "vitb8"))
+    parser.add_argument('--freeze_encoder', action='store_true')
     args = parser.parse_args()
 
     USE_CUDA = torch.cuda.is_available()
-    device = torch.device("cuda:0" if USE_CUDA else "cpu")
+    device = torch.device("cuda" if USE_CUDA else "cpu")
 
+    # Create logging folders
     if not os.path.exists(args.save_dir):
[…]

### 2022-03-27 train.sh

@@ -1,0 +1,8 @@
+python ./train.py \
+    --content_dir ./datasets/coco \
+    --style_dir ./datasets/wikiart \
+    --vgg ./weights/vgg_normalised.pth \
+    --batch_size 8 \
+    --n_threads 4 \
+    --save_model_interval 10000 \
+    --dino_encoder none

### 2022-03-27 ImageDataset.py
moved Dataset to separate file

@@ -1,0 +1,33 @@
+import os
+from glob import glob
+from PIL import Image
+import torch.utils.data as data
+from torchvision import transforms
+
+def train_transform():
+    transform_list = [
+        transforms.Resize(size=(512, 512)),
+        transforms.RandomCrop(256),
+        transforms.ToTensor()
+    ]
+    return transforms.Compose(transform_list)
+
+class ImageDataset(data.Dataset):
+    def __init__(self, root, transform):
+        super(ImageDataset, self).__init__()
+        self.root = root
+        print("Creating Dataset from", self.root)
+        self.paths = glob(os.path.join(self.root, "**/*.*"), recursive=True)
+        self.transform = transform
+
+    def __getitem__(self, index):
+        path = self.paths[index]
+        img = Image.open(str(path)).convert('RGB')
+        img = self.transform(img)
+        return img
+
+    def __len__(self):
+        return len(self.paths)
+        
+    def name(self):
+        return 'ImageDataset'

### 2022-03-27 train.py

@@ -11,48 +11,14 @@ from pathlib import Path
 import torch
 import torch.nn as nn
 import torch.utils.data as data
-from torchvision import transforms
 from torchvision.utils import save_image
-from PIL import Image
-from PIL import ImageFile
 from tensorboardX import SummaryWriter
 
 import models.transformer as transformer
-import models.StyTR  as StyTR 
+import models.StyTR  as StyTR
+from ImageDataset import ImageDataset
+from ImageDataset import train_transform
 from sampler import InfiniteSamplerWrapper
-
-def train_transform():
-    transform_list = [
-        transforms.Resize(size=(512, 512)),
-        transforms.RandomCrop(256),
-        transforms.ToTensor()
-    ]
-    return transforms.Compose(transform_list)
-
-
-class FlatFolderDataset(data.Dataset):
-    def __init__(self, root, transform):
-        super(FlatFolderDataset, self).__init__()
-        self.root = root
-        print(self.root)
-        self.path = os.listdir(self.root)
-        if os.path.isdir(os.path.join(self.root,self.path[0])):
-            self.paths = []
-            for file_name in os.listdir(self.root):
-                for file_name1 in os.listdir(os.path.join(self.root,file_name)):
-                    self.paths.append(self.root+"/"+file_name+"/"+file_name1)             
-        else:
-            self.paths = list(Path(self.root).glob('*'))
-        self.transform = transform
-    def __getitem__(self, index):
-        path = self.paths[index]
-        img = Image.open(str(path)).convert('RGB')
-        img = self.transform(img)
-        return img
-    def __len__(self):
-        return len(self.paths)
-    def name(self):
-        return 'FlatFolderDataset'
 
 def adjust_learning_rate(optimizer, iteration_count):
     """Imitating the original implementation"""
@@ -130,12 +96,12 @@ if __name__ == '__main__':
 
     network.to(device)
     #network = nn.DataParallel(network, device_ids=[0,1])  # Don't use DataParallel
-    content_tf = train_transform()
-    style_tf = train_transform()
 
     ### Create Dataset and DataLoader ###
-    content_dataset = FlatFolderDataset(args.content_dir, content_tf)
-    style_dataset = FlatFolderDataset(args.style_dir, style_tf)
+    content_tf = train_transform()
+    style_tf = train_transform()
+    content_dataset = ImageDataset(args.content_dir, content_tf)
+    style_dataset = ImageDataset(args.style_dir, style_tf)
 
[…]

### 2022-03-28 models/StyTR.py
moved loss calculation to train file

@@ -2,38 +2,17 @@ import torch
 import torch.nn.functional as F
 from torch import nn
 import numpy as np
+
 from util import box_ops
 from util.misc import (NestedTensor, nested_tensor_from_tensor_list,
                        accuracy, get_world_size, interpolate,
                        is_dist_avail_and_initialized)
 from function import normal,normal_style
 from function import calc_mean_std
-import scipy.stats as stats
+import models.transformer as transformer
 from models.ViT_helper import DropPath, to_2tuple, trunc_normal_
 
-class PatchEmbed(nn.Module):
-    """ Image to Patch Embedding
-    """
-    def __init__(self, img_size=256, patch_size=8, in_chans=3, embed_dim=512):
-        super().__init__()
-        img_size = to_2tuple(img_size)
-        patch_size = to_2tuple(patch_size)
-        num_patches = (img_size[1] // patch_size[1]) * (img_size[0] // patch_size[0])
-        self.img_size = img_size
-        self.patch_size = patch_size
-        self.num_patches = num_patches
-        
-        self.proj = nn.Conv2d(in_chans, embed_dim, kernel_size=patch_size, stride=patch_size)
-        self.up1 = nn.Upsample(scale_factor=2, mode='nearest')
-
-    def forward(self, x):
-        B, C, H, W = x.shape
-        x = self.proj(x)
-
-        return x
-
-
-decoder = nn.Sequential(
+cnn_decoder = nn.Sequential(
     nn.ReflectionPad2d((1, 1, 1, 1)),
     nn.Conv2d(512, 256, (3, 3)),
     nn.ReLU(),
@@ -121,8 +100,34 @@ vgg = nn.Sequential(
     nn.ReLU()  # relu5-4
 )
 
+
+class PatchEmbed(nn.Module):
+    """ 
+    Image to Patch Embedding
+    """
+    def __init__(self, img_size=256, patch_size=8, in_chans=3, embed_dim=512):
+        super().__init__()
+        img_size = to_2tuple(img_size)
+        patch_size = to_2tuple(patch_size)
+        num_patches = (img_size[1] // patch_size[1]) * (img_size[0] // patch_size[0])
+        self.img_size = img_size
+        self.patch_size = patch_size
+        self.num_patches = num_patches
+        
+        self.proj = nn.Conv2d(in_chans, embed_dim, kernel_size=patch_size, stride=patch_size)
[…]

### 2022-03-28 train.py

@@ -1,7 +1,5 @@
 """
 TODO: add DINO training as a possible thing through a flag
-
-TODO: add loss function here, take it out of the model
 """
 
 import argparse
@@ -10,11 +8,12 @@ from tqdm import tqdm
 from pathlib import Path
 import torch
 import torch.nn as nn
+import torch.nn.functional as F
 import torch.utils.data as data
 from torchvision.utils import save_image
 from tensorboardX import SummaryWriter
 
-import models.transformer as transformer
+from function import calc_mean_std, normal, normal_style
 import models.StyTR  as StyTR
 from ImageDataset import ImageDataset
 from ImageDataset import train_transform
@@ -32,6 +31,55 @@ def warmup_learning_rate(optimizer, iteration_count):
     # print(lr)
     for param_group in optimizer.param_groups:
         param_group['lr'] = lr
+
+def calc_style_loss(input, target):
+    assert (input.size() == target.size())
+    assert (target.requires_grad is False)
+    input_mean, input_std = calc_mean_std(input)
+    target_mean, target_std = calc_mean_std(target)
+    return F.mse_loss(input_mean, target_mean) + F.mse_loss(input_std, target_std)
+
+def calc_content_loss(input, target):
+    assert (input.size() == target.size())
+    assert (target.requires_grad is False)
+    return F.mse_loss(input, target)
+
+def get_loss(model, vgg, content_input, style_input):
+    """
+    Calculate the loss function
+        - Ics: Image output created from content and style
+        - loss_c: Content perceptual loss
+        - loss_s: Style perceptual loss
+        - loss_lambda1: Identity loss between Icc and Ic, Iss and Is
+        - loss_lambda2: Identity loss between VGG features of Icc and Ic, Iss and Is
+    """
+    Ics = model(content_input, style_input)
+    Icc = model(content_input, content_input)
+    Iss = model(style_input, style_input)
+    with torch.no_grad():
+        content_feats = vgg(content_input)
+        style_feats = vgg(style_input)
+        Ics_feats = vgg(Ics)
+        Icc_feats = vgg(Icc)
+        Iss_feats = vgg(Iss)
+
+    # Content Perceptual Loss
+    loss_c = calc_content_loss(normal(Ics_feats[-1]), normal(content_feats[-1])) + calc_content_loss(normal(Ics_feats[-2]), normal(content_feats[-2]))
+    
[…]

### 2022-03-28 models/StyTR.py
functionality to use DINO encoder

@@ -112,10 +112,8 @@ class PatchEmbed(nn.Module):
         num_patches = (img_size[1] // patch_size[1]) * (img_size[0] // patch_size[0])
         self.img_size = img_size
         self.patch_size = patch_size
-        self.num_patches = num_patches
-        
+        self.num_patches = num_patches        
         self.proj = nn.Conv2d(in_chans, embed_dim, kernel_size=patch_size, stride=patch_size)
-        self.up1 = nn.Upsample(scale_factor=2, mode='nearest')
 
     def forward(self, x):
         B, C, H, W = x.shape
@@ -178,9 +176,39 @@ class StyTrans(nn.Module):
         Initialize the main model.
         """
         super().__init__()
-        self.transformer = transformer.Transformer()    
-        self.decode = cnn_decoder
         self.embedding = PatchEmbed()
+        self.transformer = transformer.Transformer(dino_encoder=args.dino_encoder)    
+        self.decode = nn.Sequential(
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(self.transformer.d_model, 256, (3, 3)),
+            nn.ReLU(),
+            nn.Upsample(scale_factor=2, mode='nearest'),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(256, 256, (3, 3)),
+            nn.ReLU(),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(256, 256, (3, 3)),
+            nn.ReLU(),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(256, 256, (3, 3)),
+            nn.ReLU(),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(256, 128, (3, 3)),
+            nn.ReLU(),
+            nn.Upsample(scale_factor=2, mode='nearest'),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(128, 128, (3, 3)),
+            nn.ReLU(),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
+            nn.Conv2d(128, 64, (3, 3)),
+            nn.ReLU(),
+            nn.Upsample(scale_factor=2, mode='nearest'),
+            nn.ReflectionPad2d((1, 1, 1, 1)),
[…]

### 2022-03-28 models/transformer.py

@@ -7,24 +7,49 @@ from torch import nn, Tensor
 from function import normal,normal_style
 import numpy as np
 import os
-device = torch.device("cuda:2" if torch.cuda.is_available() else "cpu")
-os.environ["CUDA_VISIBLE_DEVICES"] = "2, 3"
+
+
+class DINOTransformer(nn.Module):
+    """
+    Because I need to override the DINO forward function
+    """
+    def __init__(self, pretrained):
+        super().__init__()
+        self.dino = torch.hub.load('facebookresearch/dino:main', 'dino_' + pretrained)
+        self.embed_dim = self.dino.embed_dim
+
+    def forward(self, x):
+        x = self.dino.prepare_tokens(x)
+        for blk in self.dino.blocks:
+            x = blk(x)
+        x = self.dino.norm(x)
+        return x[:, 1:]
+
+
 class Transformer(nn.Module):
 
     def __init__(self, d_model=512, nhead=8, num_encoder_layers=3,
                  num_decoder_layers=3, dim_feedforward=2048, dropout=0.1,
                  activation="relu", normalize_before=False,
-                 return_intermediate_dec=False):
+                 return_intermediate_dec=False, dino_encoder="none"):
         super().__init__()
 
-        encoder_layer = TransformerEncoderLayer(d_model, nhead, dim_feedforward,
-                                                dropout, activation, normalize_before)
-        encoder_norm = nn.LayerNorm(d_model) if normalize_before else None
+        self.dino_encoder = dino_encoder
+        if dino_encoder == "none":
+            print("Creating Traditional Transformer Encoder")
+            encoder_layer = TransformerEncoderLayer(d_model, nhead, dim_feedforward,
+                                                    dropout, activation, normalize_before)
+            encoder_norm = nn.LayerNorm(d_model) if normalize_before else None
+            self.encoder_c = TransformerEncoder(encoder_layer, num_encoder_layers, encoder_norm)
+            self.encoder_s = TransformerEncoder(encoder_layer, num_encoder_layers, encoder_norm)
+        else:
+            print("Using DINO Pretrained ViT As Encoder")
+            self.encoder_c = DINOTransformer(dino_encoder)
+            self.encoder_s = DINOTransformer(dino_encoder)
         
-        # TODO: these encoders are the things we talked about in our proposal
-        # replaye with DINO through a flag
[…]

### 2022-03-28 train.py

@@ -155,8 +155,14 @@ if __name__ == '__main__':
         num_workers=args.n_threads))
     
     ### Create Optimizer (Jimmy Baaaaaaa) ###
+    if args.freeze_encoder:
+        for param in network.transformer.encoder_c.parameters():
+            param.requires_grad = False
+        for param in network.transformer.encoder_s.parameters():
+            param.requires_grad = False
+
     optimizer = torch.optim.Adam([ 
-                                {'params': network.transformer.parameters()},
+                                {'params': filter(lambda p: p.requires_grad, network.transformer.parameters())},
                                 {'params': network.decode.parameters()},
                                 {'params': network.embedding.parameters()},        
                                 ], lr=args.lr)
@@ -188,8 +194,8 @@ if __name__ == '__main__':
               "-style:", loss_s.sum().cpu().detach().numpy(), "-l1:", l_identity1.sum().cpu().detach().numpy(), "-l2:", l_identity2.sum().cpu().detach().numpy()
              )
 
-        # save logging images to test folder every 100 iterations
-        if i % 100 == 0:
+        # save logging images to test folder every 1000 iterations
+        if i % 1000 == 0:
             print('learning_rate: %s' % str(optimizer.param_groups[0]['lr']))
             output_name = '{:s}/test/{:s}{:s}'.format(
                             args.save_dir, str(i),".jpg"

### 2022-03-28 train.py
small bug fixes

@@ -112,6 +112,8 @@ if __name__ == '__main__':
     # add additional flags for other experiments
     parser.add_argument('--dino_encoder', default="none", type=str, help="Use a pretrained DINO encoder", choices=("none", "vits16", "vits8", "vitb16", "vitb8"))
     parser.add_argument('--freeze_encoder', action='store_true')
+
+    parser.add_argument('--amp', action='store_true', help="Use Automatic Mixed Precision (to help with batch sizes)")
     args = parser.parse_args()
 
     USE_CUDA = torch.cuda.is_available()
@@ -167,6 +169,10 @@ if __name__ == '__main__':
                                 {'params': network.embedding.parameters()},        
                                 ], lr=args.lr)
 
+    if args.amp:
+        print("Using Automatic Mixed Precision")
+        scaler = torch.cuda.amp.GradScaler()
+
     ### Training Loop ###
     for i in tqdm(range(args.max_iter)):
         # learning rate strategy
@@ -181,28 +187,27 @@ if __name__ == '__main__':
         style_images = next(style_iter).to(device) 
 
         # pass through model and get loss
-        out, loss_c, loss_s, l_identity1, l_identity2 = get_loss(network, vgg, content_images, style_images) 
+        if args.amp:
+            with torch.cuda.amp.autocast():
+                out, loss_c, loss_s, l_identity1, l_identity2 = get_loss(network, vgg, content_images, style_images) 
+        else:
+            out, loss_c, loss_s, l_identity1, l_identity2 = get_loss(network, vgg, content_images, style_images) 
             
         loss_c = args.content_weight * loss_c
         loss_s = args.style_weight * loss_s
         loss = loss_c + loss_s + (l_identity1 * 70) + (l_identity2 * 1)
 
-        loss.sum().backward()
-        optimizer.step()
+        if args.amp:
+            scaler.scale(loss.sum()).backward()
+            scaler.step(optimizer)
+            scaler.update()
+        else:
+            loss.sum().backward()
+            optimizer.step()
     
         print("Loss:", loss.sum().cpu().detach().numpy(), "-content:", loss_c.sum().cpu().detach().numpy(), 
               "-style:", loss_s.sum().cpu().detach().numpy(), "-l1:", l_identity1.sum().cpu().detach().numpy(), "-l2:", l_identity2.sum().cpu().detach().numpy()
              )
-
-        # save logging images to test folder every 1000 iterations
[…]

### 2022-03-28 train.sh

@@ -1,8 +1,9 @@
 python ./train.py \
-    --content_dir ./datasets/coco \
-    --style_dir ./datasets/wikiart \
+    --content_dir ./datasets/cocotrain2014_small \
+    --style_dir ./datasets/wikiart_small \
     --vgg ./weights/vgg_normalised.pth \
+    --max_iter 1000 \
     --batch_size 8 \
     --n_threads 4 \
-    --save_model_interval 10000 \
+    --save_model_interval 500 \
     --dino_encoder none

### 2022-03-28 models/StyTR.py
deleted excess

@@ -12,38 +12,6 @@ from function import calc_mean_std
 import models.transformer as transformer
 from models.ViT_helper import DropPath, to_2tuple, trunc_normal_
 
-cnn_decoder = nn.Sequential(
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(512, 256, (3, 3)),
-    nn.ReLU(),
-    nn.Upsample(scale_factor=2, mode='nearest'),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(256, 256, (3, 3)),
-    nn.ReLU(),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(256, 256, (3, 3)),
-    nn.ReLU(),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(256, 256, (3, 3)),
-    nn.ReLU(),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(256, 128, (3, 3)),
-    nn.ReLU(),
-    nn.Upsample(scale_factor=2, mode='nearest'),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(128, 128, (3, 3)),
-    nn.ReLU(),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(128, 64, (3, 3)),
-    nn.ReLU(),
-    nn.Upsample(scale_factor=2, mode='nearest'),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(64, 64, (3, 3)),
-    nn.ReLU(),
-    nn.ReflectionPad2d((1, 1, 1, 1)),
-    nn.Conv2d(64, 3, (3, 3)),
-)
-
 vgg = nn.Sequential(
     nn.Conv2d(3, 3, (1, 1)),
     nn.ReflectionPad2d((1, 1, 1, 1)),

### 2022-03-28 ImageDataset.py
bug fixes and gradient accumulation

@@ -22,7 +22,16 @@ class ImageDataset(data.Dataset):
 
     def __getitem__(self, index):
         path = self.paths[index]
-        img = Image.open(str(path)).convert('RGB')
+        img = None
+        while img is None:
+            # while loop to get around bad image read problems
+            try:
+                img = Image.open(str(path)).convert('RGB')
+            except:
+                # get a different one
+                index = index + 10
+                path = self.paths[(index) % len(self.paths)]
+
         img = self.transform(img)
         return img
 

### 2022-03-28 train.py

@@ -28,7 +28,6 @@ def adjust_learning_rate(optimizer, iteration_count):
 def warmup_learning_rate(optimizer, iteration_count):
     """Imitating the original implementation"""
     lr = args.lr * 0.1 * (1.0 + 3e-4 * iteration_count)
-    # print(lr)
     for param_group in optimizer.param_groups:
         param_group['lr'] = lr
 
@@ -113,7 +112,10 @@ if __name__ == '__main__':
     parser.add_argument('--dino_encoder', default="none", type=str, help="Use a pretrained DINO encoder", choices=("none", "vits16", "vits8", "vitb16", "vitb8"))
     parser.add_argument('--freeze_encoder', action='store_true')
 
+    # additional flags for training implemented
     parser.add_argument('--amp', action='store_true', help="Use Automatic Mixed Precision (to help with batch sizes)")
+    parser.add_argument('--save_img_interval', type=int, default=1000)
+    parser.add_argument('--gradient_accum_steps', type=int, default=1, help="Number of steps to accumulate gradients over")
     args = parser.parse_args()
 
     USE_CUDA = torch.cuda.is_available()
@@ -180,7 +182,6 @@ if __name__ == '__main__':
             warmup_learning_rate(optimizer, iteration_count=i)
         else:
             adjust_learning_rate(optimizer, iteration_count=i)
-        optimizer.zero_grad()
 
         # get images from dataloaders
         content_images = next(content_iter).to(device)
@@ -195,17 +196,22 @@ if __name__ == '__main__':
             
         loss_c = args.content_weight * loss_c
         loss_s = args.style_weight * loss_s
-        loss = loss_c + loss_s + (l_identity1 * 70) + (l_identity2 * 1)
+        loss = (loss_c + loss_s + (l_identity1 * 70) + (l_identity2 * 1)).sum() / args.gradient_accum_steps
 
         if args.amp:
-            scaler.scale(loss.sum()).backward()
-            scaler.step(optimizer)
-            scaler.update()
+            scaler.scale(loss).backward()
+            if i % args.gradient_accum_steps == 0:
+                scaler.step(optimizer)
+                scaler.update()
+                optimizer.zero_grad()
+
         else:
-            loss.sum().backward()
-            optimizer.step()
+            loss.backward()
+            if i % args.gradient_accum_steps == 0:
+                optimizer.step()
[…]

### 2022-04-15 main_dino.py
experiment 3 trains

@@ -447,7 +447,7 @@ class DataAugmentationDINO(object):
 
         # first global crop
         self.global_transfo1 = transforms.Compose([
-            transforms.RandomResizedCrop(224, scale=global_crops_scale,
+            transforms.RandomResizedCrop(256, scale=global_crops_scale,
                                          interpolation=Image.BICUBIC),
             flip_and_color_jitter,
             utils.GaussianBlur(1.0),
@@ -455,7 +455,7 @@ class DataAugmentationDINO(object):
         ])
         # second global crop
         self.global_transfo2 = transforms.Compose([
-            transforms.RandomResizedCrop(224, scale=global_crops_scale,
+            transforms.RandomResizedCrop(256, scale=global_crops_scale,
                                          interpolation=Image.BICUBIC),
             flip_and_color_jitter,
             utils.GaussianBlur(0.1),

### 2022-04-15 models/StyTR.py

@@ -186,29 +186,60 @@ class StyTrans(nn.Module):
             nn.Conv2d(64, 3, (3, 3)),
         )
 
-    def forward(self, samples_c: NestedTensor, samples_s: NestedTensor):
+    def forward(self, samples_c: NestedTensor, samples_s: NestedTensor, skip_c_encoder=False, skip_s_encoder=True):
         """
         The forward expects a NestedTensor, which consists of:
             - samples.tensor: batched images, of shape [batch_size x 3 x H x W]
             - samples.mask: a binary mask of shape [batch_size x H x W], containing 1 on padded pixels
         """
-        if isinstance(samples_c, (list, torch.Tensor)):
-            # support different-sized images padding is used for mask [tensor, mask]
-            samples_c = nested_tensor_from_tensor_list(samples_c)
-        if isinstance(samples_s, (list, torch.Tensor)):
-            samples_s = nested_tensor_from_tensor_list(samples_s)
-
-        # Linear projection
-        # NOTE: no PatchEmbedding needed if using DINO ViT since those have that built in
-        if self.transformer.dino_encoder == "none":
-            style = self.embedding(samples_s.tensors)
-            content = self.embedding(samples_c.tensors)
+        if skip_c_encoder:
+            content = samples_c
         else:
-            style = samples_s.tensors
-            content = samples_c.tensors
+            if isinstance(samples_c, (list, torch.Tensor)):
+                # support different-sized images padding is used for mask [tensor, mask]
+                samples_c = nested_tensor_from_tensor_list(samples_c)
+            if self.transformer.dino_encoder == "none":
+                content = self.embedding(samples_c.tensors)
+            else:
+                content = samples_c.tensors
+
+        if skip_s_encoder:
+            style = samples_s
+        else:
+            if isinstance(samples_s, (list, torch.Tensor)):
+                samples_s = nested_tensor_from_tensor_list(samples_s)
+            # Linear projection
+            # NOTE: no PatchEmbedding needed if using DINO ViT since those have that built in
+            if self.transformer.dino_encoder == "none":
+                style = self.embedding(samples_s.tensors)
+            else:
+                style = samples_s.tensors
+
         pos_s = None
         pos_c = None
         mask = None
 
-        Ics = self.decode(self.transformer(style, mask, content, pos_c, pos_s))
[…]

### 2022-04-15 models/transformer.py

@@ -75,30 +75,36 @@ class Transformer(nn.Module):
             for p in self.decoder.parameters():
                 if p.dim() > 1:
                     nn.init.xavier_uniform_(p)
+    
+    def forward(self, style, mask, content, pos_embed_c, pos_embed_s, skip_c_encoder=False, skip_s_encoder=False):
+        # skip_s_encoder and skip_c_encoder indicate whether style & content should
+        # be passed through encoders.
+        if not skip_c_encoder:
+            if self.dino_encoder == "none":
+                # content-aware positional embedding
+                content_pool = self.averagepooling(content)
+                pos_c = self.new_ps(content_pool)
+                pos_embed_c = F.interpolate(pos_c, mode='bilinear', size=style.shape[-2:])
 
-    def forward(self, style, mask, content, pos_embed_c, pos_embed_s):
-        if self.dino_encoder == "none":
-            # content-aware positional embedding
-            content_pool = self.averagepooling(content)
-            pos_c = self.new_ps(content_pool)
-            pos_embed_c = F.interpolate(pos_c, mode='bilinear', size=style.shape[-2:])
-
-            # flatten NxCxHxW to HWxNxC
-            style = style.flatten(2).permute(2, 0, 1)
-            if pos_embed_s is not None:
-                pos_embed_s = pos_embed_s.flatten(2).permute(2, 0, 1)
-
-            content = content.flatten(2).permute(2, 0, 1)
-            if pos_embed_c is not None:
-                pos_embed_c = pos_embed_c.flatten(2).permute(2, 0, 1)
-
-            style = self.encoder_s(style, src_key_padding_mask=mask, pos=pos_embed_s)
-            content = self.encoder_c(content, src_key_padding_mask=mask, pos=pos_embed_c)
-        else:
-            style = self.encoder_s(style)
-            content = self.encoder_c(content)
-            style = style.permute(1, 0, 2)
-            content = content.permute(1, 0, 2)
+                content = content.flatten(2).permute(2, 0, 1)
+                if pos_embed_c is not None:
+                    pos_embed_c = pos_embed_c.flatten(2).permute(2, 0, 1)
+                
+                content = self.encoder_c(content, src_key_padding_mask=mask, pos=pos_embed_c)
+            else:
+                content = self.encoder_c(content)
[…]

### 2022-04-15 train.py

@@ -6,6 +6,7 @@ import argparse
 import os
 from pathlib import Path
 
+import numpy as np
 import torch
 import torch.nn as nn
 import torch.nn.functional as F
@@ -16,13 +17,14 @@ from torchvision.utils import save_image
 from tqdm import tqdm
 
 import models.StyTR as StyTR
+from models.transformer import Transformer, TransformerEncoder
 import util.dino_utils as utils
+from util.misc import nested_tensor_from_tensor_list
 import vision_transformer as vits
 from function import calc_mean_std, normal, normal_style
 from ImageDataset import ImageDataset, train_transform
-from main_dino import DataAugmentationDINO, DINOLoss, get_args_parser
+from main_dino import DataAugmentationDINO
 from sampler import InfiniteSamplerWrapper
-from vision_transformer import DINOHead
 
 
 def adjust_learning_rate(optimizer, iteration_count):
@@ -53,7 +55,7 @@ def calc_content_loss(input, target):
     return F.mse_loss(input, target)
 
 
-def get_loss(model, vgg, content_input, style_input):
+def get_loss(model, vgg, content_input, style_input, origin_content, origin_style, skip_c_encoder=False, skip_s_encoder=False):
     """
     Calculate the loss function
         - Ics: Image output created from content and style
@@ -61,13 +63,14 @@ def get_loss(model, vgg, content_input, style_input):
         - loss_s: Style perceptual loss
         - loss_lambda1: Identity loss between Icc and Ic, Iss and Is
         - loss_lambda2: Identity loss between VGG features of Icc and Ic, Iss and Is
+        - ready_images: (Ics, Icc, Iss) that are already calculated. default=none
     """
-    Ics = model(content_input, style_input)
-    Icc = model(content_input, content_input)
-    Iss = model(style_input, style_input)
+    Ics = model(content_input, style_input, skip_c_encoder, skip_s_encoder)
+    Icc = model(content_input, content_input, skip_c_encoder, skip_s_encoder)
+    Iss = model(style_input, style_input, skip_c_encoder, skip_s_encoder)
     with torch.no_grad():
-        content_feats = vgg(content_input)
-        style_feats = vgg(style_input)
+        content_feats = vgg(origin_content)
+        style_feats = vgg(origin_style)
         Ics_feats = vgg(Ics)
         Icc_feats = vgg(Icc)
         Iss_feats = vgg(Iss)
@@ -82,7 +85,7 @@ def get_loss(model, vgg, content_input, style_input):
[…]

### 2022-04-15 train.py
setup for experiment 4

@@ -4,6 +4,7 @@ TODO: add DINO training as a possible thing through a flag
 
 import argparse
 import os
+import sys
 from pathlib import Path
 
 import numpy as np
@@ -17,14 +18,14 @@ from torchvision.utils import save_image
 from tqdm import tqdm
 
 import models.StyTR as StyTR
-from models.transformer import Transformer, TransformerEncoder
 import util.dino_utils as utils
-from util.misc import nested_tensor_from_tensor_list
 import vision_transformer as vits
 from function import calc_mean_std, normal, normal_style
 from ImageDataset import ImageDataset, train_transform
 from main_dino import DataAugmentationDINO
+from models.transformer import Transformer, TransformerEncoder
 from sampler import InfiniteSamplerWrapper
+from util.misc import nested_tensor_from_tensor_list
 
 
 def adjust_learning_rate(optimizer, iteration_count):
@@ -96,12 +97,14 @@ def get_loss(model, vgg, content_input, style_input, origin_content, origin_styl
 
     return Ics.detach(), loss_c, loss_s, loss_lambda1, loss_lambda2
 
+
 def encoder_pre_process(sample_images, embedding):
     if isinstance(sample_images, (list, torch.Tensor)):
         sample_images = nested_tensor_from_tensor_list(sample_images)
 
     result = embedding(sample_images.tensors).flatten(2).permute(2, 0, 1)
     return result
+
 
 class DINOLoss_new(nn.Module):
     def __init__(self, warmup_teacher_temp, teacher_temp,
@@ -153,6 +156,7 @@ class DINOLoss_new(nn.Module):
 
         # ema update
         self.center = self.center * self.center_momentum + batch_center * (1 - self.center_momentum)
+
 
 def resize_image(images, new_hw, kernel):
     """
@@ -208,7 +212,7 @@ if __name__ == '__main__':
     parser.add_argument('--dino_c_encoder_training', type=utils.bool_flag, default=False,
                         help="Use the dino training procedure for the content encoder")
     parser.add_argument('--dino_encoder_loss', default="none", type=str,
-                        help="If using the dino training procedure, decide which loss to use", choices=("none", "embedded"))
+                        help="If using the dino training procedure, decide which loss to use", choices=("none", "embedded", "target"))
 
     # additional flags for training implemented
     parser.add_argument('--amp', action='store_true',
@@ -228,7 +232,6 @@ if __name__ == '__main__':
     parser.add_argument('--warmup_teacher_temp_epochs', default=0, type=int,
[…]

### 2022-04-15 train_1.sh

@@ -10,10 +10,7 @@ python ./train.py \
     --style_dir ./datasets/wikiart_small \
     --vgg ./weights/vgg_normalised.pth \
     --max_iter 1000 \
-    --batch_size 4 \
-    --n_threads 2 \
+    --batch_size 8 \
+    --n_threads 4 \
     --save_model_interval 500 \
-    --dino_encoder none \
-    --dino_c_encoder_training True \
-    --dino_s_encoder_training True \
-    --dino_encoder_loss embedded
+    --dino_encoder none

### 2022-04-15 train.py
small fixes about devices and no_grad

@@ -66,8 +66,8 @@ def get_loss(model, vgg, content_input, style_input, origin_content, origin_styl
         - ready_images: (Ics, Icc, Iss) that are already calculated. default=none
     """
     Ics = model(content_input, style_input, skip_c_encoder, skip_s_encoder)
-    Icc = model(content_input, content_input, skip_c_encoder, skip_s_encoder)
-    Iss = model(style_input, style_input, skip_c_encoder, skip_s_encoder)
+    Icc = model(content_input, content_input, skip_c_encoder, skip_c_encoder)
+    Iss = model(style_input, style_input, skip_s_encoder, skip_s_encoder)
     with torch.no_grad():
         content_feats = vgg(origin_content)
         style_feats = vgg(origin_style)
@@ -274,6 +274,8 @@ if __name__ == '__main__':
     teacher_transformer = Transformer(dino_encoder="none")
     teacher_encoder_c = teacher_transformer.encoder_c
     teacher_encoder_s = teacher_transformer.encoder_s
+    teacher_encoder_s.to(device)
+    teacher_encoder_c.to(device)
 
     student_encoder_c = network.transformer.encoder_c
     student_encoder_s = network.transformer.encoder_s
@@ -395,7 +397,8 @@ if __name__ == '__main__':
                     student_encoding_c = resize_image(student_encoding_c, student_c_out[ind - 1].size(0), 21)
                 student_c_out.append(student_encoding_c)
                 if ind < 2:
-                    teacher_c_out.append(teacher_encoder_c(c_images_batch))
+                    with torch.no_grad():
+                        teacher_c_out.append(teacher_encoder_c(c_images_batch))
             # compute dino loss
             student_c_out = torch.stack(student_c_out)
             teacher_c_out = torch.stack(teacher_c_out)
@@ -419,7 +422,8 @@ if __name__ == '__main__':
                     student_encoding_s = resize_image(student_encoding_s, student_s_out[ind - 1].size(0), 21)
                 student_s_out.append(student_encoding_s)
                 if ind < 2:
-                    teacher_s_out.append(teacher_encoder_s(s_images_batch))
+                    with torch.no_grad():
+                        teacher_s_out.append(teacher_encoder_s(s_images_batch))
             student_s_out = torch.stack(student_s_out)
             teacher_s_out = torch.stack(teacher_s_out)
             dino_s_loss = dino_s_loss_func(student_s_out, teacher_s_out, i)

### 2022-04-15 train.py
moved things to gpu

@@ -169,7 +169,7 @@ def resize_image(images, new_hw, kernel):
     C = images.size(1)
     hw = images.size(2)
     p = (new_hw + kernel - 1 - hw) // 2
-    conv = nn.Conv1d(in_channels=C, out_channels=C, kernel_size=kernel, padding=p)
+    conv = nn.Conv1d(in_channels=C, out_channels=C, kernel_size=kernel, padding=p).to(device)
     resized_im = conv(images)
     return resized_im.permute(2, 0, 1)
 
@@ -395,7 +395,7 @@ if __name__ == '__main__':
             # apply teacher and student to each of the dino-preprocessed image
             # teacher is only applied to the first two global views
             for ind, c_images_batch in enumerate(dino_content_images):
-                c_images_batch.to(device)
+                c_images_batch = c_images_batch.to(device)
                 c_images_batch = encoder_pre_process(c_images_batch, network.embedding)
                 student_encoding_c = student_encoder_c(c_images_batch)
                 if ind >= 2:
@@ -422,7 +422,7 @@ if __name__ == '__main__':
             student_s_out = []
             teacher_s_out = []
             for ind, s_images_batch in enumerate(dino_style_images):
-                s_images_batch.to(device)
+                s_images_batch = s_images_batch.to(device)
                 s_images_batch = encoder_pre_process(s_images_batch, network.embedding)
                 student_encoding_s = student_encoder_s(s_images_batch)
                 if ind >= 2:

### 2022-04-15 train_2.sh

@@ -6,11 +6,18 @@ then
 fi
 
 python ./train.py \
-    --content_dir ./datasets/cocotrain2014_small \
-    --style_dir ./datasets/wikiart_small \
+    --content_dir ./datasets/cocotrain2014 \
+    --style_dir ./datasets/wikiart \
     --vgg ./weights/vgg_normalised.pth \
-    --max_iter 1000 \
-    --batch_size 8 \
+    --save_dir ./experiment2 \
+    --log_dir ./logs2 \
+    --lr_decay 5e-6 \
+    --max_iter 320000 \
+    --batch_size 4 \
     --n_threads 4 \
-    --save_model_interval 500 \
-    --dino_encoder none
+    --save_model_interval 50000 \
+    --dino_encoder vits8 \
+    --freeze_encoder_s \
+    --freeze_encoder_c \
+    --gradient_accum_steps 2 \
+    --amp

### 2022-04-15 models/transformer.py
alternative dino loss

@@ -75,7 +75,7 @@ class Transformer(nn.Module):
             for p in self.decoder.parameters():
                 if p.dim() > 1:
                     nn.init.xavier_uniform_(p)
-    
+
     def forward(self, style, mask, content, pos_embed_c, pos_embed_s, skip_c_encoder=False, skip_s_encoder=False):
         # skip_s_encoder and skip_c_encoder indicate whether style & content should
         # be passed through encoders.
@@ -89,12 +89,12 @@ class Transformer(nn.Module):
                 content = content.flatten(2).permute(2, 0, 1)
                 if pos_embed_c is not None:
                     pos_embed_c = pos_embed_c.flatten(2).permute(2, 0, 1)
-                
+
                 content = self.encoder_c(content, src_key_padding_mask=mask, pos=pos_embed_c)
             else:
                 content = self.encoder_c(content)
                 content = content.permute(1, 0, 2)
-        
+
         if not skip_s_encoder:
             if self.dino_encoder == "none":
                 # flatten NxCxHxW to HWxNxC

### 2022-04-15 train.py

@@ -67,8 +67,8 @@ def get_loss(model, vgg, content_input, style_input, origin_content, origin_styl
         - ready_images: (Ics, Icc, Iss) that are already calculated. default=none
     """
     Ics = model(content_input, style_input, skip_c_encoder, skip_s_encoder)
-    Icc = model(content_input, content_input, skip_c_encoder, skip_s_encoder)
-    Iss = model(style_input, style_input, skip_c_encoder, skip_s_encoder)
+    Icc = model(content_input, content_input, skip_c_encoder, skip_c_encoder)
+    Iss = model(style_input, style_input, skip_s_encoder, skip_s_encoder)
     with torch.no_grad():
         content_feats = vgg(origin_content)
         style_feats = vgg(origin_style)
@@ -161,7 +161,7 @@ class DINOLoss_new(nn.Module):
 def resize_image(images, new_hw, kernel):
     """
     expect images to have shape (HW, N, C)
-    apply 1-D convolution to resize image to 
+    apply 1-D convolution to resize image to
     (new_hw, N, C)
     """
     # permute shape to (N, C, HW)
@@ -295,14 +295,18 @@ if __name__ == '__main__':
 
     # ======== image preprocessing modules and datasets for dino method ======== #
 
+    skip_s_encoder = args.dino_s_encoder_training or args.dino_encoder_loss == "target"
+    skip_c_encoder = args.dino_c_encoder_training or args.dino_encoder_loss == "target"
+
     if args.dino_s_encoder_training:
         dino_style_tf = DataAugmentationDINO(
             args.global_crops_scale,
             args.local_crops_scale,
             args.local_crops_number,
         )
-        skip_s_encoder = True
+
         dino_style_dataset = ImageDataset(args.style_dir, dino_style_tf)
+        n = ImageDataset(args.style_dir, dino_style_tf)
 
         dino_style_iter = iter(data.DataLoader(
             dino_style_dataset, batch_size=args.batch_size,
@@ -315,7 +319,6 @@ if __name__ == '__main__':
             args.local_crops_scale,
             args.local_crops_number,
         )
-        skip_c_encoder = True
         dino_content_dataset = ImageDataset(args.content_dir, dino_content_tf)
 
         dino_content_iter = iter(data.DataLoader(
@@ -402,15 +405,46 @@ if __name__ == '__main__':
                 student_c_out.append(student_encoding_c)
                 if ind < 2:
[…]

### 2022-04-15 train.py
stupid error

@@ -444,8 +444,6 @@ if __name__ == '__main__':
                 student_c_out = torch.stack(student_c_out)
                 teacher_c_out = torch.stack(teacher_c_out)
 
-                print(student_c_out[0].shape)
-
                 dino_c_loss = dino_c_loss_func(student_c_out, teacher_c_out, i)
         elif args.dino_encoder_loss != "target":
             model_content_in = origin_content_images
@@ -503,8 +501,6 @@ if __name__ == '__main__':
             else:
                 student_c_out = torch.stack(student_c_out)
                 teacher_c_out = torch.stack(teacher_c_out)
-
-                print(student_c_out[0].shape)
 
                 dino_c_loss = dino_c_loss_func(student_c_out, teacher_c_out, i)
         elif args.dino_encoder_loss != "target":

### 2022-04-15 train.py
loss issue

@@ -502,7 +502,7 @@ if __name__ == '__main__':
                 student_c_out = torch.stack(student_c_out)
                 teacher_c_out = torch.stack(teacher_c_out)
 
-                dino_c_loss = dino_c_loss_func(student_c_out, teacher_c_out, i)
+                dino_c_loss = dino_s_loss_func(student_c_out, teacher_c_out, i)
         elif args.dino_encoder_loss != "target":
             model_style_in = origin_style_images
 

### 2022-04-15 train.py
bug fixes

@@ -486,8 +486,9 @@ if __name__ == '__main__':
 
                 student_images = network(student_c_out, student_s_out,
                                          skip_c_encoder, skip_s_encoder)
-                teacher_images = network(teacher_c_out, teacher_s_out,
-                                         skip_c_encoder, skip_s_encoder)
+                with torch.no_grad():
+                    teacher_images = network(teacher_c_out, teacher_s_out,
+                                            skip_c_encoder, skip_s_encoder)
 
                 shape = student_images.shape
                 student_images = student_images.view(
@@ -499,10 +500,12 @@ if __name__ == '__main__':
 
                 dino_s_loss = dino_s_loss_func(student_images, teacher_images, i)
             else:
-                student_c_out = torch.stack(student_c_out)
-                teacher_c_out = torch.stack(teacher_c_out)
+                if isinstance(student_c_out, tuple):
+                    student_c_out = torch.stack(student_c_out)
+                if isinstance(teacher_c_out, tuple):
+                    teacher_c_out = torch.stack(teacher_c_out)
 
-                dino_c_loss = dino_s_loss_func(student_c_out, teacher_c_out, i)
+                dino_s_loss = dino_s_loss_func(student_c_out, teacher_c_out, i)
         elif args.dino_encoder_loss != "target":
             model_style_in = origin_style_images
 

### 2022-04-15 train_3.sh
turned off cotent dino flag

@@ -14,6 +14,6 @@ python ./train.py \
     --n_threads 2 \
     --save_model_interval 500 \
     --dino_encoder none \
-    --dino_c_encoder_training True \
+    --dino_c_encoder_training False \
     --dino_s_encoder_training True \
     --dino_encoder_loss embedded

### 2022-04-15 models/transformer.py
fixed bugs about training flags

@@ -84,7 +84,10 @@ class Transformer(nn.Module):
                 # content-aware positional embedding
                 content_pool = self.averagepooling(content)
                 pos_c = self.new_ps(content_pool)
-                pos_embed_c = F.interpolate(pos_c, mode='bilinear', size=style.shape[-2:])
+                if not skip_s_encoder:
+                    pos_embed_c = F.interpolate(pos_c, mode='bilinear', size=style.shape[-2:])
+                else:
+                    pos_embed_c = F.interpolate(pos_c, mode='bilinear', size=content.shape[-2:])
 
                 content = content.flatten(2).permute(2, 0, 1)
                 if pos_embed_c is not None:

### 2022-04-15 train.py

@@ -499,13 +499,11 @@ if __name__ == '__main__':
                     (shape[0] // args.batch_size, args.batch_size) + (shape[1:]))
 
                 dino_s_loss = dino_s_loss_func(student_images, teacher_images, i)
-            else:
-                if isinstance(student_c_out, tuple):
-                    student_c_out = torch.stack(student_c_out)
-                if isinstance(teacher_c_out, tuple):
-                    teacher_c_out = torch.stack(teacher_c_out)
+            else: 
+                student_s_out = torch.stack(student_s_out)
+                teacher_s_out = torch.stack(teacher_s_out)
 
-                dino_s_loss = dino_s_loss_func(student_c_out, teacher_c_out, i)
+                dino_s_loss = dino_s_loss_func(student_s_out, teacher_s_out, i)
         elif args.dino_encoder_loss != "target":
             model_style_in = origin_style_images
 

### 2022-04-15 train_3.sh

@@ -14,6 +14,6 @@ python ./train.py \
     --n_threads 2 \
     --save_model_interval 500 \
     --dino_encoder none \
-    --dino_c_encoder_training False \
-    --dino_s_encoder_training True \
+    --dino_c_encoder_training True \
+    --dino_s_encoder_training False \
     --dino_encoder_loss embedded

### 2022-04-16 train_3.sh
reverse flags

@@ -14,6 +14,6 @@ python ./train.py \
     --n_threads 2 \
     --save_model_interval 500 \
     --dino_encoder none \
-    --dino_c_encoder_training True \
-    --dino_s_encoder_training False \
+    --dino_c_encoder_training False \
+    --dino_s_encoder_training True \
     --dino_encoder_loss embedded

### 2022-04-16 paper/Paper.tex
stuff for the paper

@@
 
-% if you need to pass options to natbib, use, e.g.:
-%     \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2021
+\PassOptionsToPackage{numbers, compress}{natbib}
 
-% ready for submission
-\usepackage{neurips_2021}
+\usepackage[final]{paper_neurips_2021}
 
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%     \usepackage[preprint]{neurips_2021}
+\bibliographystyle{abbrvnat}
 
-% to compile a camera-ready version, add the [final] option, e.g.:
-%     \usepackage[final]{neurips_2021}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{hyperref}
+\usepackage{url}
+\usepackage{booktabs}
+\usepackage{amsfonts}
+\usepackage{nicefrac}
+\usepackage{microtype}
+\usepackage{xcolor}
 
-% to avoid loading the natbib package, add option nonatbib:
-%    \usepackage[nonatbib]{neurips_2021}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{xcolor}         % colors
-
-\title{Formatting Instructions For NeurIPS 2021}
+\title{DINO Methods for Style Transfer}
 
@@
 \author{
-  David S.~Hippocampus\thanks{Use footnote for providing further information
-    about author (webpage, alternative address)---\emph{not} for acknowledging
-    funding agencies.} \\
+	Sacha Goldman \\
 	Department of Computer Science\\ 
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
-  % examples of more authors
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \AND
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
+	Department of Mathematics\\
+	University of Toronto\\
+	Toronto, ON M5S 1A1 \\
+	\texttt{sacha.goldman@mail.utoronto.ca} \\
+	\And
+	Yuchong Zhang \\
+	Department of Computer Science \\
+	Department of Mathematics \\
+	University of Toronoto \\
+	Toronto, ON, M5S 1A1 \\
+	\texttt{yuchongz.zhang@mail.utoronto.ca} \\
+	\And
+	Shirley Wang \\
+	Department of Computer Science \\
+	University of Toronto \\
+	Toronto, ON M5S 1A1 \\
+	\texttt{shirlsyuemeng.wang@mail.utoronto.ca} \\
 }
@@
 \begin{abstract}
-  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
-  both the left- and right-hand margins. Use 10~point type, with a vertical
-  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
-  bold, and in point size 12. Two line spaces precede the abstract. The abstract
-  must be limited to one paragraph.
+We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr2 \cite{ImageStyleTransformer}, a style transfer transformer that renders images with artistic style, and explore the nature and robustness of the resulting model.
 \end{abstract}
 
-\section{Submission of papers to NeurIPS 2021}
+\section{Introduction}
+Style transfer is the problem of changing an image's artistic style while maintaining its ``content'', namely the object it depicts.
+Conventional models use a CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image.
+However, it has been shown that due to the locality resulting from shared weights, CNN based models struggle to capture global information of input images and suffer from feature losses \cite{ImageStyleTransformer}.
+To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results \cite{ImageStyleTransformer}.
+The model StyTr2 proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder.
+In our project, we will substitute the DINO method and models from \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
+The DINO method is good at extracting content even if the input images are distorted or partial, so in particular, we will implement the models and conduct experiments to explore the following questions:
+\begin{enumerate}
+	\item By using DINO to extract content, can we obtain a style transfer that is more robust to distortion of the content image?
+	\item Does DINO's ability to capture an image's global property from local pieces give it more robustness as a style encoder?
+	\item Are the results of this new style transfer method better than previous methods?
+\end{enumerate}
 
-Please read the instructions below carefully and follow them faithfully.
+\section{Related Works}
 
-\subsection{Style}
+\cite{DINO} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student paradigm.
+The student gets a difficult version (lots of augmentation) of the image while the teacher gets an easy version (minimal augmentation), and then the models are trained to aim for the same feature representation through cross entropy loss.
+Their experimental results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing as very accurate classifiers.
+In this project, we aim to apply the better feature representation that the DINO method yields (over supervised vision transformers), to the domain of image style transfer.
 
-Papers to be submitted to NeurIPS 2021 must be prepared according to the
-instructions presented here. Papers may only be up to {\bf nine} pages long,
-including figures. Additional pages \emph{containing only acknowledgments and
-references} are allowed. Papers that exceed the page limit will not be
-reviewed, or in any other way considered for presentation at the conference.
+Self-supervised learning is a common technique used in style transfer, due to the obvious lack of target images available for a task of this nature.
+It becomes necessary to find ways for the model to supervise its own outputs.
+Usual methods \cite{CNNStyleTransfer} involve checking the outputs of VGG for consistency in style and context.
+\cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
+Transformers have been a hot rising topic in computer vision, and they claim that their method of using transformers for style transfer results in a decrease in content leak, as well as acheives unbiased stylization.
 
-The margins in 2021 are the same as those in 2007, which allow for $\sim$$15\%$
-more words in the paper compared to earlier years.
+It becomes integral for there to be good feature representations of the content and style to construct a good style-transferred image.
+We believe that making use of pretrained DINO ViT models, as well as using the DINO method itself during training, can help achieve this.
 
-Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
-NeurIPS website as indicated below. Please make sure you use the current files
-and not previous versions. Tweaking the style files may be grounds for
-rejection.
+\section{Method}
 
-\subsection{Retrieval of style files}
+We have four different ideas for bringing the success of the DINO method to the style transfer task.
 
-The style files for NeurIPS and other conference information are available on
-the World Wide Web at
-\begin{center}
-  \url{http://www.neurips.cc/}
-\end{center}
-The file \verb+neurips_2021.pdf+ contains these instructions and illustrates the
-various formatting requirements your NeurIPS paper must satisfy.
+\subsection{Frozen DINO Content Encoder}
 
-The only supported style file for NeurIPS 2021 is \verb+neurips_2021.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
-  Microsoft Word, and RTF are no longer supported!}
+We initialize the content encoder with the DINO pretrained vision transformer and freeze its weights.
+Then we train the style encoder and decoder using the regular style transfer training paradigm from \cite{ImageStyleTransformer}.
+The idea being that the DINO model's robust feature vectors may act as powerful abstractions of the content of the images, that can be used for creating a new stylized image.
 
-The \LaTeX{} style file contains three optional arguments: \verb+final+, which
-creates a camera-ready copy, \verb+preprint+, which creates a preprint for
-submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
-\verb+natbib+ package for you in case of package clash.
+\subsection{Initial Pretrained DINO Content Encoder}
 
-\paragraph{Preprint option}
-If you wish to post a preprint of your work online, e.g., on arXiv, using the
-NeurIPS style, please use the \verb+preprint+ option. This will create a
-nonanonymized version of your work with the text ``Preprint. Work in progress.''
-in the footer. This version may be distributed as you see fit. Please \textbf{do
-  not} use the \verb+final+ option, which should \textbf{only} be used for
-papers accepted to NeurIPS.
+We initialize the content encoder with the DINO pretrained vision transformer, but we run the style transfer training paradigm on both encoders and the decoder.
+We expect this to converge to a different optima because transformers have many local optima.
+We hope that the robust abstractions from the DINO training process lead to better style transfer after training.
 
-At submission time, please omit the \verb+final+ and \verb+preprint+
-options. This will anonymize your submission and add line numbers to aid
-review. Please do \emph{not} refer to these line numbers in your paper as they
-will be removed during generation of camera-ready copies.
+\subsection{DINO Training for Encoders}
 
-The file \verb+neurips_2021.tex+ may be used as a ``shell'' for writing your
-paper. All you have to do is replace the author, title, abstract, and text of
-the paper with your own.
+For the purpose of DINO training we add a teacher content encoder and a teacher style encoder.
+Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images.
+We then add together the loss from the standard style transfer and the cross entropy loss between the teacher encodings and the student encodings.
+This forces the students to learn distillations of the original images.
+We expect this to work better for the style encoder, because style is a global property of an image, so we may only apply this method for the style encoder.
 
-The formatting instructions contained in these style files are summarized in
-Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
+\subsection{Modified DINO Training for Encoders}
 
-\section{General formatting instructions}
-\label{gen_inst}
+This method is similar to the previous, except that instead of taking the cross entropy between the encodings, we take apply the decoder transformer to the encodings from both the teacher and student encoders, which would yield a teacher image and a student image.
+We then use the distance between the teacher image and the student image in our loss.
+The precise distance metric used here is to be determined through experimentation.
+This will allow the encoders to distill the important pieces of the stylized image.
+This method may suffer from being very expensive to train.
+We also may only apply this to the style encoder.
 
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
-type with a vertical spacing (leading) of 11~points.  Times New Roman is the
-preferred typeface throughout, and will be selected for you by default.
-Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
-indentation.
+\section{Experiments}
 
-The paper title should be 17~point, initial caps/lower case, bold, centered
-between two horizontal rules. The top rule should be 4~points thick and the
-bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
-below the title to rules. All pages should start at 1~inch (6~picas) from the
-top of the page.
+\subsection{Implementation Details}
 
-For the final version, authors' names are set in boldface, and each name is
-centered above the corresponding address. The lead author's name is to be listed
-first (left-most), and the co-authors' names (if different address) are set to
-follow. If there is only one co-author, list both author and co-author side by
-side.
+MS-COCO [cite] is used as the content dataset and WikiArt [cite] is used as the style dataset. In the training stage,
+all the images are randomly cropped into a fixed resolution of 256 × 256, while any image resolution is supported at the test time.
+We used the Adam optimizer [cite] and a warm-up adjustment strategy [cite] is used.
+Our GPU is not as big as the one used in the original paper, so while we could not train with their batch size, we modified the learning rate decay, number of iterations trained, and gradient accumulation steps to mimic the original's training process of a batch size of 8 for 160,000 iterations.
+Gradients are also clipped to a maximum norm of 10 to prevent exploding gradients.
 
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
+\subsection{Qualitative Evaluation}
 
-\section{Headings: first level}
-\label{headings}
+\subsection{Comparisons with SOTA Methods}
 
-All headings should be lower case (except for first word and proper nouns),
-flush left, and bold.
+\subsubsection{Timing Information}
 
-First-level headings should be in 12-point type.
+\subsubsection{Qualitative Evaluation}
 
-\subsection{Headings: second level}
+\subsubsection{Quantitative Evaluation}
 
-Second-level headings should be in 10-point type.
+\section{Conclusion}
 
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the heading in
-bold, flush left, and inline with the text, with the heading followed by 1\,em
-of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.  Citations may be
-author/year or numeric, as long as you maintain internal consistency.  As to the
-format of the references themselves, any style is acceptable as long as it is
-used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations appropriate for
-use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may add the
-following before loading the \verb+neurips_2021+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add the optional
-argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{neurips_2021}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the third
-person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
-previous work [4].'' If you cite your other papers that are not widely available
-(e.g., a journal paper under review), use anonymous author names in the
-citation, e.g., an author of the form ``A.\ Anonymous.''
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote, indicate
-footnotes with a number\footnote{Sample of the first footnote.} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-\begin{figure}
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-All artwork must be neat, clean, and legible. Lines should be dark enough for
-purposes of reproduction. The figure number and caption always appear after the
-figure. Place one line space before the figure caption and one line space after
-the figure. The figure caption should be lower case (except for first word and
-proper nouns); figures are numbered consecutively.
-
-You may use color figures.  However, it is best for the figure captions and the
-paper body to be legible if the paper is printed in either black/white or in
-color.
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table number and
-title always appear before the table.  See Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical rules.} We
-strongly suggest the use of the \verb+booktabs+ package, which allows for
-typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule(r){1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style files.  In
-particular, do not modify the width or length of the rectangle the text should
-fit into, and do not change font sizes (except perhaps in the
-\textbf{References} section; see below). Please note that pages should be
-numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and not, for
-example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file must only
-contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
-achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
-  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
-  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
-  available out-of-the-box on most Linux machines.
-
-\item The IEEE has recommendations for generating PDF files whose fonts are also
-  acceptable for NeurIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
-  "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
-  the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
-for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
-workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
-you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
-figure width as a multiple of the line width as in the example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
-necessary.
-
-\begin{ack}
-Use unnumbered first level headings for the acknowledgments. All acknowledgments
-go at the end of the paper before the list of references. Moreover, you are required to declare
-funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2021/PaperInformation/FundingDisclosure}.
-
-Do {\bf not} include this section in the anonymized submission, only in the final paper.
-You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
-\end{ack}
-
-\section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-when listing the references.
-Note that the Reference section does not count towards the page limit.
 \medskip
 
-{
-\small
+% Our current sources
+\nocite{*}
 
-[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
-connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
-(eds.), {\it Advances in Neural Information Processing Systems 7},
-pp.\ 609--616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
-  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
-TELOS/Springer--Verlag.
-
-[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
-recall at excitatory recurrent synapses and cholinergic modulation in rat
-hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Checklist}
-
-%%% BEGIN INSTRUCTIONS %%%
-The checklist follows the references.  Please
-read the checklist guidelines carefully for information on how to answer these
-questions.  For each question, change the default \answerTODO{} to \answerYes{},
-\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
-justification to your answer}, either by referencing the appropriate section of
-your paper or providing a brief inline description.  For example:
-\begin{itemize}
-  \item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
-  \item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
-  \item Did you include the license to the code and datasets? \answerNA{}
-\end{itemize}
-Please do not modify the questions and only use the provided macros for your
-answers.  Note that the Checklist section does not count towards the page
-limit.  In your paper, please delete this instructions block and only keep the
-Checklist section heading above along with the questions/answers below.
-%%% END INSTRUCTIONS %%%
-
-\begin{enumerate}
-
-\item For all authors...
-\begin{enumerate}
-  \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
-    \answerTODO{}
-  \item Did you describe the limitations of your work?
-    \answerTODO{}
-  \item Did you discuss any potential negative societal impacts of your work?
-    \answerTODO{}
-  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
-    \answerTODO{}
-\end{enumerate}
-
-\item If you are including theoretical results...
-\begin{enumerate}
-  \item Did you state the full set of assumptions of all theoretical results?
-    \answerTODO{}
-	\item Did you include complete proofs of all theoretical results?
-    \answerTODO{}
-\end{enumerate}
-
-\item If you ran experiments...
-\begin{enumerate}
-  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
-    \answerTODO{}
-  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
-    \answerTODO{}
-	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
-    \answerTODO{}
-	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
-    \answerTODO{}
-\end{enumerate}
-
-\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
-\begin{enumerate}
-  \item If your work uses existing assets, did you cite the creators?
-    \answerTODO{}
-  \item Did you mention the license of the assets?
-    \answerTODO{}
-  \item Did you include any new assets either in the supplemental material or as a URL?
-    \answerTODO{}
-  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
-    \answerTODO{}
-  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
-    \answerTODO{}
-\end{enumerate}
-
-\item If you used crowdsourcing or conducted research with human subjects...
-\begin{enumerate}
-  \item Did you include the full text of instructions given to participants and screenshots, if applicable?
-    \answerTODO{}
-  \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
-    \answerTODO{}
-  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
-    \answerTODO{}
-\end{enumerate}
-
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{bib}
 

### 2022-04-19 paper/Paper.tex
Fixed styling things
small change to method

@@
 
-\section{Method}
+\section{Methods}
 
-We have four different ideas for bringing the success of the DINO method to the style transfer task.
+\subsection{DINO Pretrained ViT Content Encoder}
 
-\subsection{Frozen DINO Content Encoder}
-
-We initialize the content encoder with the DINO pretrained vision transformer and freeze its weights.
-Then we train the style encoder and decoder using the regular style transfer training paradigm from \cite{ImageStyleTransformer}.
-The idea being that the DINO model's robust feature vectors may act as powerful abstractions of the content of the images, that can be used for creating a new stylized image.
-
-\subsection{Initial Pretrained DINO Content Encoder}
-
-We initialize the content encoder with the DINO pretrained vision transformer, but we run the style transfer training paradigm on both encoders and the decoder.
-We expect this to converge to a different optima because transformers have many local optima.
-We hope that the robust abstractions from the DINO training process lead to better style transfer after training.
+The DINO paper provided their Vision Transformers that were trained using their proposed method.
+We attempted to use these models as a starting point for the content and style encoders of the model in three different ways: A) Freezing the weights for both the content and style encoders, B) Freezing only the weights for the content encoder, and C) letting both the content and style encoders train with the rest of the network.
 

### 2022-04-19 paper/Paper.tex
experiments ABC qualitative analysis

@@
 
-\usepackage[final]{paper_neurips_2021}
+\usepackage[preprint]{neurips_2021}
 
@@
 \subsection{Qualitative Evaluation}
+In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image.
+But in both cases, certain details of the objects depicted in the content image are lost.
+For experiment A, we can see both the content and style losses decrease over time.
+Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.
+
+Experiment C failed to learn style transfer.
+At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image.
+After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are.
+As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.
 

### 2022-04-19 paper/Paper.tex
finished 4.2

@@
 In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image.
-But in both cases, certain details of the objects depicted in the content image are lost.
+But in both cases, certain details of the objects depicted in the content image are lost with experiment B being better at preserving features.
 For experiment A, we can see both the content and style losses decrease over time.
@@
 As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.
+
+During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image.
+The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some occasional color losses.
+We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.
+
+Finally, experiment E also failed.
+In early stages of the training, the model renders the content with many colored vertical strips and many features were lost.
+Eventually, the model started to output single-color images.
+We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.
 

### 2022-04-19 paper/Paper.tex
First draft of method

@@
 \usepackage{xcolor}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{enumitem}
+\usepackage{mathrsfs}
+\usepackage{graphicx}
+\usepackage{scrextend}
+\usepackage{hyperref}
+\usepackage{tikz}
+\usepackage{bm}
 
@@
 	Department of Mathematics \\
-	University of Toronoto \\
+	University of Toronto \\
 	Toronto, ON, M5S 1A1 \\
@@
 Self-supervised learning is a common technique used in style transfer, due to the obvious lack of target images available for a task of this nature.
-It becomes necessary to find ways for the model to supervise its own outputs.
+It becomes necessary to find ways for the model to supervise its own outfputs.
 Usual methods \cite{CNNStyleTransfer} involve checking the outputs of VGG for consistency in style and context.
 \cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
-Transformers have been a hot rising topic in computer vision, and they claim that their method of using transformers for style transfer results in a decrease in content leak, as well as acheives unbiased stylization.
+Transformers have been a hot rising topic in computer vision, and they claim that their method of using transformers for style transfer results in a decrease in content leak, as well as achieves unbiased stylization.
 
@@
 
-For the purpose of DINO training we add a teacher content encoder and a teacher style encoder.
-Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images.
-We then add together the loss from the standard style transfer and the cross entropy loss between the teacher encodings and the student encodings.
+To translate the success of DINO training on classification to style transfer we modify our algorithm and architecture.
+Now instead of simple a style encoder, there is a teacher style encoder $SE_t$ and a student style encoder $SE_s$, both using the architecture from $\cite{ImageStyleTransformer}$.
 This forces the students to learn distillations of the original images.
-We expect this to work better for the style encoder, because style is a global property of an image, so we may only apply this method for the style encoder.
+Because style is a global property of an image, we applied this only to the style encoder and left the content encoder $CE$ as in $\cite{ImageStyleTransformer}$.
 
-\subsection{Modified DINO Training for Encoders}
+To train this model, as in the \cite{DINO}, from the original style image we generate two slightly modified global views of the image $(I_s)^g_1$ and $(I_s)^g_2$ as well as a collection more heavily modified local views, with the set of all views denoted $V$.
+The student is passed all the views whereas the teacher is only passed the global views.
+We then calculate
+\begin{align}
+	\mathcal L_d &= \sum_{I \in \{(I_s)^g_1, (I_s)^g_2\}} \sum_{I' \in V - \{ I \}} H(SE_t(I), SE_s(I'))
+\end{align} 
+Where $H(a,b) = -a \log (b)$.
+This loss is what forces our student style encoder to learn these distilled representations.
+We can average $SE_s((I_s)^g_1)$ and $SE_s(I_s)^g_2$ to get the encoded style, and we can take $CE(I_c)$ to get the content.
+From this we can generate $I_o$, the output image, using the decoder $D$.
+We can also pass the style to both inputs of $D$ to get $I_{ss}$ and similarly we get $I_{cc}$.
+Now we can use $\mathcal L_c$, $\mathcal L_s$, $\mathcal L_{id1}$,$\mathcal L_{id2}$ from $\cite{ImageStyleTransformer}$.
+We can then combine these into the final loss
+\begin{align}
+	\mathcal L &= \lambda_d \mathcal L_d + \lambda_c \mathcal L_c + \lambda_s \mathcal L_s + \lambda_{id1} \mathcal L_{id1} + \lambda_{id2} \mathcal L_{id2}
+\end{align}
+where the $\lambda$'s are weightings. We call this model D).
 
-This method is similar to the previous, except that instead of taking the cross entropy between the encodings, we take apply the decoder transformer to the encodings from both the teacher and student encoders, which would yield a teacher image and a student image.
-We then use the distance between the teacher image and the student image in our loss.
-The precise distance metric used here is to be determined through experimentation.
-This will allow the encoders to distill the important pieces of the stylized image.
-This method may suffer from being very expensive to train.
-We also may only apply this to the style encoder.
+We also define model E) where we modify (1) to
+\begin{align}
+	\mathcal L_d &= \sum_{I \in \{(I_s)^g_1, (I_s)^g_2\}} \sum_{I' \in V - \{ I \}} H(D(SE_t(I), CE(I_c)), D(SE_s(I'), CE(I_c))).
+\end{align}
+Where calculating the loss after the decoder should weight the most relevant student and teacher differences higher.
 
@@
 We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.
-
 \subsection{Comparisons with SOTA Methods}

### 2022-04-19 paper/Paper.tex
small fix

@@
 To translate the success of DINO training on classification to style transfer we modify our algorithm and architecture.
-Now instead of simple a style encoder, there is a teacher style encoder $SE_t$ and a student style encoder $SE_s$, both using the architecture from $\cite{ImageStyleTransformer}$.
+Now instead of simple a style encoder, there is a teacher style encoder $SE_t$ and a student style encoder $SE_s$, both using the architecture from \cite{ImageStyleTransformer}.
 This forces the students to learn distillations of the original images.
-Because style is a global property of an image, we applied this only to the style encoder and left the content encoder $CE$ as in $\cite{ImageStyleTransformer}$.
+Because style is a global property of an image, we applied this only to the style encoder and left the content encoder $CE$ as in \cite{ImageStyleTransformer}.
 
@@
 We can also pass the style to both inputs of $D$ to get $I_{ss}$ and similarly we get $I_{cc}$.
-Now we can use $\mathcal L_c$, $\mathcal L_s$, $\mathcal L_{id1}$,$\mathcal L_{id2}$ from $\cite{ImageStyleTransformer}$.
+Now we can use $\mathcal L_c$, $\mathcal L_s$, $\mathcal L_{id1}$,$\mathcal L_{id2}$ from \cite{ImageStyleTransformer}.
 We can then combine these into the final loss
@@
 
-\appendix
-
-\section{Appendix}
-
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
-
 \end{document}

### 2022-04-19 paper/Paper.tex
added image

@@
 MS-COCO [cite] is used as the content dataset and WikiArt [cite] is used as the style dataset. In the training stage,
-all the images are randomly cropped into a fixed resolution of 256 × 256, while any image resolution is supported at the test time.
+all the images are randomly cropped into a fixed resolution of 256 x 256, while any image resolution is supported at the test time.
 We used the Adam optimizer [cite] and a warm-up adjustment strategy [cite] is used.
@@
 \subsection{Qualitative Evaluation}
+
+\includegraphics[scale=0.35]{comparison}
+
 In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image.
@@
 We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.
-\subsection{Comparisons with SOTA Methods}
+
+\subsection{Comparisons with Other Methods}
 

### 2022-04-19 paper/Paper.tex
just quantitative
combined 4.2 with figure

@@
 
+\begin{figure}
 	\includegraphics[scale=0.35]{comparison}
+	\caption{Style transfer results across different experiments.}
+	\label{stylefig}
+\end{figure}
 
 In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image.
-But in both cases, certain details of the objects depicted in the content image are lost with experiment B being better at preserving features.
+But in both cases, certain details of the objects depicted in the content image are lost.
+Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{stylefig}).
 For experiment A, we can see both the content and style losses decrease over time.
-Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.
+Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscilating more.
 
@@
 At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image.
-After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are.
+After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are (column C, figure \ref{stylefig}).
 As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.
@@
 During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image.
-The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some occasional color losses.
+The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{stylefig}).
 We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.
@@
 In early stages of the training, the model renders the content with many colored vertical strips and many features were lost.
-Eventually, the model started to output single-color images.
+Eventually, the model started to output single-color images (column E, figure \ref{stylefig}).
 We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.

### 2022-04-19 paper/Paper.tex
combined 4.2 with figure

@@
 	\caption{Style transfer results across different experiments.}
-	\label{stylefig}
+	\label{comparison}
 \end{figure}
@@
 But in both cases, certain details of the objects depicted in the content image are lost.
-Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{stylefig}).
+Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{comparison}).
 For experiment A, we can see both the content and style losses decrease over time.
@@
 At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image.
-After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are (column C, figure \ref{stylefig}).
+After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are (column C, figure \ref{comparison}).
 As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.
@@
 During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image.
-The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{stylefig}).
+The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{comparison}).
 We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.
@@
 In early stages of the training, the model renders the content with many colored vertical strips and many features were lost.
-Eventually, the model started to output single-color images (column E, figure \ref{stylefig}).
+Eventually, the model started to output single-color images (column E, figure \ref{comparison}).
 We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.
 
-\subsection{Comparisons with Other Methods}
-
-\subsubsection{Timing Information}
-
-\subsubsection{Qualitative Evaluation}
-
-\subsubsection{Quantitative Evaluation}
+\subsection{Quantitative Evaluation}
 

### 2022-04-19 models/StyTR.py
bug changes

@@ -186,7 +186,7 @@ class StyTrans(nn.Module):
             nn.Conv2d(64, 3, (3, 3)),
         )
 
-    def forward(self, samples_c: NestedTensor, samples_s: NestedTensor, skip_c_encoder=False, skip_s_encoder=True):
+    def forward(self, samples_c: NestedTensor, samples_s: NestedTensor, skip_c_encoder=False, skip_s_encoder=False):
         """
         The forward expects a NestedTensor, which consists of:
             - samples.tensor: batched images, of shape [batch_size x 3 x H x W]

### 2022-04-19 train_2.sh

@@ -11,13 +11,11 @@ python ./train.py \
     --vgg ./weights/vgg_normalised.pth \
     --save_dir ./experiment2 \
     --log_dir ./logs2 \
-    --lr_decay 5e-6 \
-    --max_iter 320000 \
-    --batch_size 4 \
+    --lr_decay 2.5e-6 \
+    --max_iter 640000 \
+    --batch_size 2 \
+    --gradient_accum_steps 4 \
     --n_threads 4 \
     --save_model_interval 50000 \
     --dino_encoder vits8 \
-    --freeze_encoder_s \
-    --freeze_encoder_c \
-    --gradient_accum_steps 2 \
     --amp

### 2022-04-19 vision_transformer.py

@@ -1,304 +1,0 @@
-"""
-NOTE: This file is only here if you want to try running main_dino.py to see how it works.
-It's not something we'll be using.
-"""
-
-
-# Copyright (c) Facebook, Inc. and its affiliates.
-#
-# Licensed under the Apache License, Version 2.0 (the "License");
-# you may not use this file except in compliance with the License.
-# You may obtain a copy of the License at
-#
-#     http://www.apache.org/licenses/LICENSE-2.0
-#
-# Unless required by applicable law or agreed to in writing, software
-# distributed under the License is distributed on an "AS IS" BASIS,
-# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-# See the License for the specific language governing permissions and
-# limitations under the License.
-"""
-Mostly copy-paste from timm library.
-https://github.com/rwightman/pytorch-image-models/blob/master/timm/models/vision_transformer.py
-"""
-
-
-
-
-import math
-from functools import partial
-import torch
-import torch.nn as nn
-from util.dino_utils import trunc_normal_
-def drop_path(x, drop_prob: float = 0., training: bool = False):
-    if drop_prob == 0. or not training:
-        return x
-    keep_prob = 1 - drop_prob
-    shape = (x.shape[0],) + (1,) * (x.ndim - 1)  # work with diff dim tensors, not just 2D ConvNets
-    random_tensor = keep_prob + torch.rand(shape, dtype=x.dtype, device=x.device)
-    random_tensor.floor_()  # binarize
-    output = x.div(keep_prob) * random_tensor
-    return output
-
-
-class DropPath(nn.Module):
-    """Drop paths (Stochastic Depth) per sample  (when applied in main path of residual blocks).
-    """
-
-    def __init__(self, drop_prob=None):
-        super(DropPath, self).__init__()
-        self.drop_prob = drop_prob
-
-    def forward(self, x):
-        return drop_path(x, self.drop_prob, self.training)
-
-
-class Mlp(nn.Module):
-    def __init__(self, in_features, hidden_features=None, out_features=None, act_layer=nn.GELU, drop=0.):
-        super().__init__()
-        out_features = out_features or in_features
-        hidden_features = hidden_features or in_features
[…]

### 2022-04-19 paper/Paper.tex
another draft

--- 2022-04-19 paper/Paper.tex
@@
 \begin{abstract}
-We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr2 \cite{ImageStyleTransformer}, a style transfer transformer that renders images with artistic style, and explore the nature and robustness of the resulting model.
+We apply DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, to style transfer by extending StyTr2 \cite{ImageStyleTransformer}, a style transfer transformer that renders images with artistic style, and explore the nature and robustness of the resulting model.
+We explore using the vision transformers pretrained with the DINO method to encode image style, and we also explore apply the DINO training methods directly to StyTr2.
+We discuss the relative qualitative and quantitative performance of our new models compared to the state of the art.
 \end{abstract}
@@
 Conventional models use a CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image.
-However, it has been shown that due to the locality resulting from shared weights, CNN based models struggle to capture global information of input images and suffer from feature losses \cite{ImageStyleTransformer}.
-To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results \cite{ImageStyleTransformer}.
-The model StyTr2 proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder.
-In our project, we will substitute the DINO method and models from \cite{DINO} for the encoder components and explore the effects on the task of style transfer.
+However, it has been shown that due to the locality resulting from shared weights, CNN based models struggle to capture the global information of input images and suffer from feature losses \cite{ImageStyleTransformer}.
+To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results, like StyTr2 \cite{ImageStyleTransformer}.
+This model takes in a content image and a style image, then uses two transformer encoders to capture the content and style, then renders the content with that style using a transformer decoder.
+In our project, we will substitute the DINO method and models from \cite{DINO} for the encoder components and explore the effects on style transfer.
 The DINO method is good at extracting content even if the input images are distorted or partial, so in particular, we will implement the models and conduct experiments to explore the following questions:
 \begin{enumerate}
-	\item By using DINO to extract content, can we obtain a style transfer that is more robust to distortion of the content image?
 	\item Does DINO's ability to capture an image's global property from local pieces give it more robustness as a style encoder?
@@
 \cite{DINO} came up with a new self-supervised learning method, named DINO (for Knowledge Distillation with No Labels) that aims to create better feature representations from its inputs by adopting a teacher-student paradigm.
-The student gets a difficult version (lots of augmentation) of the image while the teacher gets an easy version (minimal augmentation), and then the models are trained to aim for the same feature representation through cross entropy loss.
+The student gets multiple difficult views (lots of augmentation), called the local views of the image while the teacher gets an easy view (minimal augmentation), called the global view.
+Then the student is trained to aim for the same feature representation through cross entropy loss.
 Their experimental results found that the vision transformer's class token contained explicit information about the segmentation of objects in images, while also performing as very accurate classifiers.
@@
 Self-supervised learning is a common technique used in style transfer, due to the obvious lack of target images available for a task of this nature.
-It becomes necessary to find ways for the model to supervise its own outfputs.
+It becomes necessary to find ways for the model to supervise its own outputs.
 Usual methods \cite{CNNStyleTransfer} involve checking the outputs of VGG for consistency in style and context.
 \cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
-Transformers have been a hot rising topic in computer vision, and they claim that their method of using transformers for style transfer results in a decrease in content leak, as well as achieves unbiased stylization.
+Transformers have been a hot rising topic in computer vision, and they claim that their method of using transformers for style transfer results in decreased content leak, as well as achieving unbiased stylization.
 
-It becomes integral for there to be good feature representations of the content and style to construct a good style-transferred image.
+It is integral for there to be good feature representations of the content and style to construct a good style-transferred image.
 We believe that making use of pretrained DINO ViT models, as well as using the DINO method itself during training, can help achieve this.
@@
 
-\subsection{DINO Training for Encoders}
+\subsection{DINO Training the Style Encoder}
 
-To translate the success of DINO training on classification to style transfer we modify our algorithm and architecture.
-Now instead of simple a style encoder, there is a teacher style encoder $SE_t$ and a student style encoder $SE_s$, both using the architecture from \cite{ImageStyleTransformer}.
-This forces the students to learn distillations of the original images.
-Because style is a global property of an image, we applied this only to the style encoder and left the content encoder $CE$ as in \cite{ImageStyleTransformer}.
+To translate the success of DINO training on classification to style transfer we modify the algorithm and architecture of StyTr2.
+Now instead of simple transformer for the style encoder, there is a teacher style encoder $SE_t$ and a student style encoder $SE_s$, both using the architecture from \cite{ImageStyleTransformer}.
+We use the extra encoder to force the student to learn distillations of the original images.
+Because style is a global property of an image, we applied this only to the style encoder and left the content encoder $CE$ as it was in \cite{ImageStyleTransformer}.
 
-To train this model, as in the \cite{DINO}, from the original style image we generate two slightly modified global views of the image $(I_s)^g_1$ and $(I_s)^g_2$ as well as a collection more heavily modified local views, with the set of all views denoted $V$.
+To train this model, as in \cite{DINO}, from the original style image we generate two slightly modified global views of the image $(I_s)^g_1$ and $(I_s)^g_2$ as well as a collection more heavily modified local views, with the set of all views denoted $V$.
 The student is passed all the views whereas the teacher is only passed the global views.
@@
 From this we can generate $I_o$, the output image, using the decoder $D$.
-We can also pass the style to both inputs of $D$ to get $I_{ss}$ and similarly we get $I_{cc}$.
+We can also pass the encoded style to both inputs of $D$ to get $I_{ss}$ and similarly with the encoded content to get $I_{cc}$.
 Now we can use $\mathcal L_c$, $\mathcal L_s$, $\mathcal L_{id1}$,$\mathcal L_{id2}$ from \cite{ImageStyleTransformer}.
@@
 \end{align}
-where the $\lambda$'s are weightings. We call this model D).
+where the $\lambda$'s are weightings.
+We call this model D).
+We can train this using gradient based optimization, except the weights of the teacher are not updated by the gradient.
+The weights of the teacher are an exponential moving average of the students weights.
 
@@
 \end{align}
-Where calculating the loss after the decoder should weight the most relevant student and teacher differences higher.
+Hoping that calculating the loss after the decoder will weigh the most relevant differences between the student and teacher higher. Relevant meaning making a greater difference to the final issues.
 
@@
 
-\includegraphics[scale=0.35]{comparison}
+\begin{center}
+\includegraphics[width=14cm]{comparison}	
+\end{center}
 
@@
 
-\subsection{Comparisons with Other Methods}
-
-\subsubsection{Timing Information}
-
-\subsubsection{Qualitative Evaluation}
-
-\subsubsection{Quantitative Evaluation}
+\subsection{Quantitative Evaluation}
 

### 2022-04-19 paper/Paper.tex

@@
 \includegraphics[width=14cm]{comparison}	
+\caption{Style transfer results across different experiments.}
+\label{comparison}
 \end{center}
 
+\begin{figure}
+	\includegraphics[scale=0.35]{comparison}
+
+\end{figure}
+
 In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image.
-But in both cases, certain details of the objects depicted in the content image are lost with experiment B being better at preserving features.
+But in both cases, certain details of the objects depicted in the content image are lost.
+Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{comparison}).
 For experiment A, we can see both the content and style losses decrease over time.
-Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.
+Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscilating more.
 
@@
 At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image.
-After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are.
+After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are (column C, figure \ref{comparison}).
 As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.
@@
 During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image.
-The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some occasional color losses.
+The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{comparison}).
 We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.
@@
 In early stages of the training, the model renders the content with many colored vertical strips and many features were lost.
-Eventually, the model started to output single-color images.
+Eventually, the model started to output single-color images (column E, figure \ref{comparison}).
 We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.

### 2022-04-19 paper/Paper.tex
bug fix
typos

@@
 \begin{center}
+\begin{figure}
 \includegraphics[width=14cm]{comparison}	
@@
 \label{comparison}
+\end{figure}
 \end{center}
-
-\begin{figure}
-	\includegraphics[scale=0.35]{comparison}
-
-\end{figure}
 
@@
 For experiment A, we can see both the content and style losses decrease over time.
-Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscilating more.
+Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscillating more.
 
@@
 The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{comparison}).
-We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.
+We see the content loss slowly decreases as training progresses while the style loss oscillates and shows no signs of improvement.
 

### 2022-04-19 paper/Paper.tex
conclusion

@@
 
+In this paper we have shown that the transformers already trained using DINO are very useful, and we used them to achieve strong style transfer results.
+We also saw that this training method is very sensitive, and difficult to apply to new contexts.
+In future we hope to see attempts to apply this training method to other areas of computer vision, and we also hope to gain more theoretical understanding of why DINO works in some scenarios, but fails in others.
+
 \medskip

### 2022-04-19 paper/Paper.tex
code link
Open source
added experiments citations

--- 2022-04-19 paper/Paper.tex
@@
 
-MS-COCO [cite] is used as the content dataset and WikiArt [cite] is used as the style dataset. In the training stage,
+MS-COCO \cite{COCO} is used as the content dataset and WikiArt \cite{Wikiart} is used as the style dataset. In the training stage,
 all the images are randomly cropped into a fixed resolution of 256 x 256, while any image resolution is supported at the test time.
-We used the Adam optimizer [cite] and a warm-up adjustment strategy [cite] is used.
+We used the Adam optimizer \cite{Adam} and a warm-up adjustment strategy \cite{Warmup} is used.
 Our GPU is not as big as the one used in the original paper, so while we could not train with their batch size, we modified the learning rate decay, number of iterations trained, and gradient accumulation steps to mimic the original's training process of a batch size of 8 for 160,000 iterations.

### 2022-04-19 paper/Paper.tex

--- 2022-04-19 paper/Paper.tex
@@
 
-\medskip
+\let\thefootnote\relax\footnotetext{open source code: \href{https://github.com/SachaGoldman/CSC413-Project}{https://github.com/SachaGoldman/CSC413-Project}}
 

### 2022-04-19 ImageDataset.py
fixed teacher updates

@@ -4,6 +4,7 @@ from glob import glob
 import torch.utils.data as data
 from PIL import Image
 from torchvision import transforms
+import util.dino_utils as utils
 
 
 def train_transform():

### 2022-04-19 train.py

@@ -229,6 +229,9 @@ if __name__ == '__main__':
         starting with the default value of 0.04 and increase this slightly if needed.""")
     parser.add_argument('--warmup_teacher_temp_epochs', default=0, type=int,
                         help='Number of warmup epochs for the teacher temperature (Default: 30).')
+    parser.add_argument('--momentum_teacher', default=0.996, type=float, help="""Base EMA
+        parameter for teacher update. The value is increased to 1 during training with cosine schedule.
+        We recommend setting a higher value with small batches: for example use 0.9995 with batch size of 256.""")
 
     # Multi-crop parameters
     parser.add_argument('--global_crops_scale', type=float, nargs='+', default=(0.4, 1.),
@@ -284,6 +287,9 @@ if __name__ == '__main__':
 
     student_encoder_c = network.transformer.encoder_c
     student_encoder_s = network.transformer.encoder_s
+
+    momentum_schedule = utils.cosine_scheduler(args.momentum_teacher, 1,
+                                               args.max_iter, args.batch_size)
 
     # ==== flags to indicate whether encoders should be skipped when using network
     skip_s_encoder = False
@@ -546,6 +552,12 @@ if __name__ == '__main__':
             if i % args.gradient_accum_steps == 0:
                 optimizer.step()
                 optimizer.zero_grad()
+        
+        with torch.no_grad():
+            it = i + i * args.batch_size
+            m = momentum_schedule[i]  # momentum parameter
+            for param_q, param_k in zip(student_encoder_s.parameters(), teacher_encoder_s.parameters()):
+                param_k.data.mul_(m).add_((1 - m) * param_q.detach().data)
 
         print("Loss:", loss.cpu().detach().numpy() * args.gradient_accum_steps, "-content:", loss_c.sum().cpu().detach().numpy(),
               "-style:", loss_s.sum().cpu().detach().numpy(), "-l1:", l_identity1.sum(

### 2022-04-19 train_3.sh

@@ -9,11 +9,12 @@ python ./train.py \
     --content_dir ./datasets/cocotrain2014_small \
     --style_dir ./datasets/wikiart_small \
     --vgg ./weights/vgg_normalised.pth \
-    --max_iter 1000 \
-    --batch_size 4 \
-    --n_threads 2 \
+    --max_iter 200000 \
+    --batch_size 1 \
+    --n_threads 0 \
     --save_model_interval 500 \
     --dino_encoder none \
     --dino_c_encoder_training False \
     --dino_s_encoder_training True \
-    --dino_encoder_loss embedded
+    --dino_encoder_loss embedded \
+    --args.save_img_interval 100

### 2022-04-19 train_3.sh
typos

@@ -17,4 +17,4 @@ python ./train.py \
     --dino_c_encoder_training False \
     --dino_s_encoder_training True \
     --dino_encoder_loss embedded \
-    --args.save_img_interval 100
+    --save_img_interval 100

### 2022-04-19 paper/Paper.tex
quantitative analysis

--- 2022-04-19 paper/Paper.tex
@@
 We attempted to use these models as a starting point for the content and style encoders of the model in three different ways: A) Freezing the weights for both the content and style encoders, B) Freezing only the weights for the content encoder, and C) letting both the content and style encoders train with the rest of the network.
+By using the pretrained DINO ViT as a starting point, we hope to make use of the robust features this model has already learnt.
 
@@
 
-\begin{center}
 \begin{figure}
@@
 \end{figure}
-\end{center}
 
@@
 
+\begin{table}
+	\caption{Quantitative Comparison of Experiments}
+	\label{quantitative}
+	\centering
+	\begin{tabular}{lllll}
+		\toprule
+		Model     &  Content Loss & Style Loss & Identity Loss 1 & Identity Loss 2 \\
+		\midrule
+		Original Paper & 1.4133 & 0.7879 & 0.0022 & 2.4489  \\
+		Experiment A &  2.2934  & 4.6013 & 0.0139 & 18.1673  \\
+		Experiment B &  2.7997 & 2.7449 & 0.0016 & 3.1419  \\
+		Experiment C & 1.9984 & 14.4178 & 0.1529 & 33.0587  \\
+		Experiment D & 0.1304 & 7.6773 & 0.0040 & 1.0756  \\
+		Experiment E & 1.9984 & 14.2857 & 0.1531 & 32.8137  \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We created a small dataset of 100 randomly selected images from the content and style dataset, and pair them together to compute the average of the four loss terms above.
+All images are resized to 512 x 512 resolution.
+The DINO loss is left out because it is specifically between its student and teacher, and so is not relevant to performance.
+Overall, our experiment D had the best content loss and identity loss 2, although that is not particularly significant because experiment D only learnt how to copy the content image.
+Experiment A and B were the only models that successfully learned how to perform style transfer, and of the two models, only experiment B's identity loss 1 was better than the original model.
+This most likely speaks to experiment B's ability to recreate key parts of the image is better than the original papers, which probably springs from the original DINO training method's robust nature.
+
 \section{Conclusion}
@@
 In this paper we have shown that the transformers already trained using DINO are very useful, and we used them to achieve strong style transfer results.
-We also saw that this training method is very sensitive, and difficult to apply to new contexts.
+We also saw that the DINO training method is very sensitive, and difficult to apply to new contexts.
+It could be attributed to the nature of the style transfer task itself coupled with the volatile parts of self-supervised learning that caused training to explode and crash at bad local minima in many of our experiments.
+Recreating content has also been a much easier task than recreating style, as many of our failed experiments still leaned towards achieving better content loss through any means necessary, even if it was completely recreating the content image.
+
 In future we hope to see attempts to apply this training method to other areas of computer vision, and we also hope to gain more theoretical understanding of why DINO works in some scenarios, but fails in others.
 
-\medskip
+\let\thefootnote\relax\footnotetext{We have made our code freely available at: \href{https://github.com/SachaGoldman/CSC413-Project}{https://github.com/SachaGoldman/CSC413-Project}}
 

### 2022-04-22 paper/Paper.tex

@@
 \begin{abstract}
+
 We apply DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, to style transfer by extending StyTr2 \cite{ImageStyleTransformer}, a style transfer transformer that renders images with artistic style, and explore the nature and robustness of the resulting model.
@@
 We discuss the relative qualitative and quantitative performance of our new models compared to the state of the art.
+
 \end{abstract}
@@
 \section{Introduction}
+
 Style transfer is the problem of changing an image's artistic style while maintaining its ``content'', namely the object it depicts.
@@
 It becomes necessary to find ways for the model to supervise its own outputs.
-Usual methods \cite{CNNStyleTransfer} involve checking the outputs of VGG for consistency in style and context.
+Usual methods \cite{CNNStyleTransfer} \cite{ContentBlock} \cite{CycleGAN} involve checking the outputs of VGG for consistency in style and context.
 \cite{ImageStyleTransformer} proposes using vision transformers for this task, using two transformer encoders (one for content, one for style), and one transformer decoder.
@@
 The DINO paper provided their Vision Transformers that were trained using their proposed method.
-We attempted to use these models as a starting point for the content and style encoders of the model in three different ways: A) Freezing the weights for both the content and style encoders, B) Freezing only the weights for the content encoder, and C) letting both the content and style encoders train with the rest of the network.
+We attempted to use these models as a starting point for the content and style encoders of the style transfer transformer model in three different ways: A) Freezing the weights for both the content and style encoders, B) Freezing only the weights for the content encoder, and C) letting both the content and style encoders train with the rest of the network.
 By using the pretrained DINO ViT as a starting point, we hope to make use of the robust features this model has already learnt.
@@
 
-We created a small dataset of 100 randomly selected images from the content and style dataset, and pair them together to compute the average of the four loss terms above.
-All images are resized to 512 x 512 resolution.
+We created a small dataset of 100 randomly selected images from the content and style dataset, and pair them together, then pass them through each of our experiment models as well as the trained model from the original paper to compute the average of the four loss terms above.
+All images are resized to 512 x 512 resolution to avoid irregularities that occur from WikiArt images being much higher resolution than COCO images.
 The DINO loss is left out because it is specifically between its student and teacher, and so is not relevant to performance.
-Overall, our experiment D had the best content loss and identity loss 2, although that is not particularly significant because experiment D only learnt how to copy the content image.
+
 Experiment A and B were the only models that successfully learned how to perform style transfer, and of the two models, only experiment B's identity loss 1 was better than the original model.
 This most likely speaks to experiment B's ability to recreate key parts of the image is better than the original papers, which probably springs from the original DINO training method's robust nature.
+Overall, our experiment D had the best content loss and identity loss 2, although that is not particularly significant because experiment D only learnt how to copy the content image.
+While this reflects badly on the results of experiment D, it does perhaps speak to the DINO training method having some applications in autoencoders.
+Experiments C and E both got stuck at bad local minima, so they achieve bad overall loss.
 
@@
 Recreating content has also been a much easier task than recreating style, as many of our failed experiments still leaned towards achieving better content loss through any means necessary, even if it was completely recreating the content image.
-
 In future we hope to see attempts to apply this training method to other areas of computer vision, and we also hope to gain more theoretical understanding of why DINO works in some scenarios, but fails in others.
@@
 \let\thefootnote\relax\footnotetext{We have made our code freely available at: \href{https://github.com/SachaGoldman/CSC413-Project}{https://github.com/SachaGoldman/CSC413-Project}}
+
+\newpage
 
